### 2024-10-23 paper/paper.qmd
Add author and title

---
title: "Prediction of US Election in 2024"
subtitle: "My subtitle if needed"
author: 
  - Xinqi Yue
  - Yawen Tan
  - Duanyi Su
thanks: "Code and data are available at: [https://github.com/xinqiyue/2024_US_Election_Prediction](https://github.com/xinqiyue/2024_US_Election_Prediction)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-03 paper/paper.qmd
update first version of data simulation and clean

@@
 library(tidyverse)
-library(palmerpenguins)
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+president_polls_cleaned_data <- read.csv('../data/02-analysis_data/president_polls_cleaned_data.csv')
+```
+
+```{r}
+# 将日期转换为日期格式
+president_polls_cleaned_data$end_date <- ymd(president_polls_cleaned_data$end_date)
+
+# 绘图
+ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = state)) +
+  geom_point() +
+  facet_wrap(~ candidate_name, scales = "free_y") +
+  theme_minimal() +
+  #theme(legend.position = "bottom") +
+  labs(
+    y = "pct",
+    x = "end date",
+    color = "state",
+    title = "pct of Donald Trump and Kamala Harris in each states",
+  )
+
 ```
@@
 Overview paragraph
+As the United States prepares for the 2024 presidential election, the role of opinion polls in understanding voter preferences remains critical.
+Polls serve as indicators of public sentiment, offering insights into which candidates might have an advantage in the electoral race.
+This paper aims to predict the winner of the upcoming election by analyzing "poll-of-polls" data.
 
@@
 Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
-
-Talk way more about it.
 

### 2024-11-03 scripts/00-simulate_data.R

@@ -11,42 +11,32 @@
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
-
+library(dplyr)
+set.seed(666)
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
+num_rows <- 100  # Number of simulated rows
+
+president_polls <- data.frame(
+  numeric_grade = sample(2:3, num_rows, replace = TRUE),  # Numeric grades between 1 and 5
+  pollscore = rnorm(num_rows, mean = -1, sd = 0.5),  # Normally distributed poll scores
+  # methodology = sample(c("Online Panel", "Telephone", "Mixed-Mode"), num_rows, replace = TRUE),  # Poll methodologies
+  transparency_score = runif(num_rows, min = 1, max = 10),  # Uniform transparency scores between 1 and 10
+  state = sample(c("CA", "TX", "FL", "NY", ""), num_rows, replace = TRUE),  # Random states, including blank for nationwide
+  start_date = sample(seq(as.Date("2024-10-01"), as.Date("2024-10-15"), by="day"), num_rows, replace = TRUE),  # Random start dates
+  end_date = sample(seq(as.Date("2024-10-16"), as.Date("2024-10-31"), by="day"), num_rows, replace = TRUE),  # Random end dates
+  sample_size = sample(400:8000, num_rows, replace = TRUE),  # Random sample sizes between 500 and 3000
+  population = sample(c("lv", "rv"), num_rows, replace = TRUE),  # Random population groups
+  population_full = sample(c("Likely Voters", "Registered Voters"), num_rows, replace = TRUE),  # Random population full descriptions
+  hypothetical = sample(c(0, 1), num_rows, replace = TRUE),  # Random TRUE/FALSE for hypothetical
+  party = sample(c("DEM", "REP"), num_rows, replace = TRUE),  # Random party affiliations
+  answer = sample(c("Kamala Harris", "Donald Trump"), num_rows, replace = TRUE),  # Random answers
+  candidate_name = sample(c("Kamala Harris", "Donald Trump"), num_rows, replace = TRUE),  # Random candidate names
+  pct = round(runif(num_rows, min = 30, max = 60), 1)  # Random percentages between 30 and 60
 )
 
-# Political parties
[…]

### 2024-11-03 scripts/02-download_data.R

@@ -1,24 +1,17 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from 
+# Author: Rohan Alexander 
+# Date: 1 November 2023
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+# Any other information needed? 
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
-
-#### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
 president_polls_raw_data <- read.csv('data/01-raw_data/president_polls.csv')
 
 #### Save data ####
-# [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
 # write_csv(the_raw_data, "inputs/data/raw_data.csv") 
-
-         

### 2024-11-03 scripts/03-clean_data.R

@@ -9,36 +9,46 @@
 
 #### Workspace setup ####
 library(tidyverse)
-
+library(dplyr)
+library(tidyr)
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+president_polls_raw_data <- read.csv('data/01-raw_data/president_polls.csv')
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
+# 过滤出高质量民调（numeric_grade >= 2.5）的民调
+president_polls_filtered <- president_polls_raw_data %>% 
+  janitor::clean_names() %>%
+  select(pollster, numeric_grade, pollscore, methodology, transparency_score, state, 
+         start_date, end_date, sample_size, population, population_full, 
+         hypothetical, party, answer, candidate_name, pct) %>%
   tidyr::drop_na()
 
+president_polls_cleaned_data <- president_polls_filtered %>%
+  mutate(
+    hypothetical = ifelse(hypothetical == 'true', 1, 0),
+    state = if_else(is.na(state) | state == "", "National", state), 
+    end_date = mdy(end_date),
+    start_date = mdy(start_date),
+    num_candidates = round((pct / 100) * sample_size, 0) # 将百分比转换为人数
+) %>%
+  filter(numeric_grade >= 2.5
[…]

### 2024-11-03 scripts/06-model_data.R

@@ -10,12 +10,163 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(janitor)
+library(lubridate)
+library(broom)
+library(modelsummary)
 library(rstanarm)
+library(splines)
 
 #### Read data ####
 analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
 
 ### Model data ####
+#### 准备数据集 ####
+# 读取数据并清理变量名称
+president_polls_data <- read.csv('data/02-analysis_data/president_polls_cleaned_data.csv')
+
+#### 初步模型 ####
+# 模型 1：pct 作为 end_date 的函数
+model_date <- lm(pct ~ end_date, data = president_polls_cleaned_data)
+
+# 模型 2：pct 作为 end_date 和候选人的函数
+model_date_candidates <- lm(pct ~ end_date + candidate_name,
+                            #+ transparency_score + sample_size + numeric_grade + pollscore + num_candidates, 
+                            data = president_polls_cleaned_data)
+
+# 将模型预测添加到数据中
+president_polls_cleaned_data <- president_polls_cleaned_data |> 
+  mutate(
+    fitted_date = predict(model_date),
+    fitted_date_candidates = predict(model_date_candidates)
+  )
+
+# 绘制模型预测
+# 模型 1
+ggplot(president_polls_cleaned_data, aes(x = end_date)) +
+  geom_point(aes(y = pct), color = "black") +
+  geom_line(aes(y = fitted_date), color = "blue", linetype = "dotted") +
+  theme_classic() +
+  labs(y = "Candidate Support (%)", x = "Date", title = "Linear Model: pct ~ end_date")
+
+# 模型 2
+ggplot(president_polls_cleaned_data, aes(x = end_date)) +
+  geom_point(aes(y = pct, color = candidate_name)) +
+  geom_line(aes(y = fitted_date_candidates), color = "blue", linetype = "dotted") +
+  facet_wrap(vars(candidate_name)) +
+  theme_classic() +
+  labs(y = "Candidate Support (%)", x = "Date", title = "Linear Model: pct ~ end_date + candidate_name")
+
+#### 贝叶斯模型 ####
+# 将 'candidate_name' 和 'state' 转换为因子变量
+president_polls_cleaned_data <- president_polls_cleaned_data |> 
+  mutate(
[…]

### 2024-11-03 paper/paper.qmd
update data cleaning script

@@
 #| message: false
-
+# load data
 president_polls_cleaned_data <- read.csv('../data/02-analysis_data/president_polls_cleaned_data.csv')
+# transfer date to standard form
+president_polls_cleaned_data$end_date <- ymd(president_polls_cleaned_data$end_date)
 ```
@@
 ```{r}
-# 将日期转换为日期格式
-president_polls_cleaned_data$end_date <- ymd(president_polls_cleaned_data$end_date)
-
-# 绘图
+# plot graphof pct of two candidates in each state against time
 ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = state)) +
@@
   )
-
+unique(president_polls_cleaned_data$methodology)
 ```
@@
 ## Overview
+The dataset encompasses polling data focused on two candidates, Donald Trump and Kamala Harris.
+Data has been filtered to include only results from pollsters with a numeric grade above 2.5 to maintain quality and consistency.
+This selection allows us to focus on higher-rated sources, which may enhance the reliability of predictions.
+Each record includes information on the pollster, their grading, polling methodology, transparency score, and specific polling results for each candidate.
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+## Explanation of each variables
+- **pollster**: The organization that conducted the poll, providing information on who gathered the data.
 
-Overview text
+- **numeric grade**: A quality score assigned to the pollster, with higher values indicating greater reliability. Only pollsters with a score above 2.5 are included to enhance accuracy.
+
+- **pollscore**: A specific rating of the individual poll, reflecting additional factors that impact the poll's quality and reliability.
+
+- **methodology**: The method used by the pollster to conduct the poll, which may affect the reliability and interpretation of the results.
+
+- **transparency score**: A measure of how openly the pollster reports their methodology and results. Higher scores suggest greater transparency and reliability.
+
+- **state**: The U.S. state where the poll was conducted, which allows for state-by-state analysis and comparison of support levels.
+
+- **start date**: The date the poll began, marking the beginning of data collection for that specific poll.
+
+- **end date**: The date the poll concluded, marking the end of data collection for that specific poll.
+
+- **sample size**: The number of respondents in the poll, indicating the scope and potential statistical reliability of the results.
+
+- **population**: A general description of the population sampled (e.g., likely voters), providing context on who was surveyed.
+
+- **population full**: Detailed information about the sample population, offering insights into demographic or eligibility characteristics.
+
+- **hypothetical**: Indicates whether the poll was based on a hypothetical scenario, coded as a binary value.
+
+- **party**: The political party affiliation of the respondent or the focus of the poll, when specified.
+
+- **answer**: The poll outcome or response category (e.g., the candidate name or specific answer provided by respondents).
+
+- **candidate_name**: The name of the candidate being polled, which in this data set focuses on Donald Trump and Kamala Harris.
+
+- **pct**: The support percentage each candidate received in the poll, which serves as the outcome variable for analysis.
 
 ## Measurement
-
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+Key measurements in the dataset include each poll’s numeric_grade (a quality score for the pollster), pollscore (a specific rating per poll), and transparency_score.
+These indicators help assess and compare the reliability of the included poll results.
+Additionally, records contain information on sample_size, state, start_date, and end_date, capturing the timing and scope of each poll.
 
 ## Outcome variables
-
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+The primary outcome variable in this analysis is pct, representing each candidate’s support percentage in individual polls.
+Focusing on support levels for Trump and Harris enables us to evaluate current sentiment and ultimately predict the election outcome.
 
 ## Predictor variables
-
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+Predictor variables include pollster, numeric_grade, pollscore, transparency_score, state, sample_size, population, population_full, and methodology.
+These factors provide context for each poll’s results and help assess how factors such as sample size, polling method, and geographical scope may influence support percentages.
 

### 2024-11-03 scripts/00-simulate_data.R

@@ -18,21 +18,35 @@ set.seed(666)
 num_rows <- 100  # Number of simulated rows
 
 president_polls <- data.frame(
-  numeric_grade = sample(2:3, num_rows, replace = TRUE),  # Numeric grades between 1 and 5
-  pollscore = rnorm(num_rows, mean = -1, sd = 0.5),  # Normally distributed poll scores
-  # methodology = sample(c("Online Panel", "Telephone", "Mixed-Mode"), num_rows, replace = TRUE),  # Poll methodologies
-  transparency_score = runif(num_rows, min = 1, max = 10),  # Uniform transparency scores between 1 and 10
-  state = sample(c("CA", "TX", "FL", "NY", ""), num_rows, replace = TRUE),  # Random states, including blank for nationwide
-  start_date = sample(seq(as.Date("2024-10-01"), as.Date("2024-10-15"), by="day"), num_rows, replace = TRUE),  # Random start dates
+  # pollster = sample(c("Emerson", "YouGov", "Beacon/Shaw", "Quinnipiac", "SurveyUSA", "East Carolina University", "Fairleigh Dickinson", "Ipsos", "Marist", "Siena/NYT", "University of Massachusetts Lowell/YouGov", "Marquette Law School", "Hart/POS", "The Washington Post", "Pew", "Suffolk", "Mason-Dixon",
+                      #"Christopher Newport U.", "Data for Progress", "YouGov/Center for Working Class Politics", "UC Berkeley", "Winthrop U.", "High Point University", "McCourtney Institute/YouGov", "Echelon Insights", "CNN/SSRS", "AtlasIntel", "University of Maryland/Washington Post", "Remington", "Muhlenberg", 
+                      #"MassINC Polling Group", "U. New Hampshire",  "Siena", "Elon U.", "Selzer", "Data Orbital", "PPIC", "Washington Post/George Mason University", "Kaiser Family Foundation", "SurveyUSA/High Point University", "Roanoke College", "YouGov Blue", "U. North Florida"), num_rows, replace = TRUE),
+  # numeric_grade = sample(2:3, num_rows, replace = TRUE),  # Numeric grades between 1 and 5
+  # pollscore = rnorm(num_rows, mean = -1, sd = 0.5),  # Normally distributed poll scores
+  # methodology = sample(c("IVR/Online Panel/Text-to-Web", "Online Panel", "IVR/Online Panel", "Live Phone/Text-to-Web",
[…]

### 2024-11-03 scripts/01-test_simulated_data.R

@@ -26,11 +26,11 @@ if (exists("analysis_data")) {
 
 #### Test data ####
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
+# Check if the dataset has 100 rows
+if (nrow(analysis_data) == 100) {
+  message("Test Passed: The dataset has 100 rows.")
 } else {
-  stop("Test Failed: The dataset does not have 151 rows.")
+  stop("Test Failed: The dataset does not have 100 rows.")
 }
 
 # Check if the dataset has 3 columns
@@ -48,9 +48,12 @@ if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
 }
 
 # Check if the 'state' column contains only valid Australian state names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", 
-                  "Western Australia", "Tasmania", "Northern Territory", 
-                  "Australian Capital Territory")
+valid_states <- c("National", "Arizona", "California", "Georgia", "North Carolina", 
+                  "Washington", "Pennsylvania", "New Hampshire", "Texas", "Michigan", 
+                  "Nevada", "Wisconsin", "Montana", "Florida", "Ohio", "Massachusetts", "Virginia",
+                  "South Carolina", "Nebraska CD-2", "Minnesota", "New York", "Nebraska", "Maryland",
+                  "New Mexico", "Connecticut", "Rhode Island", "Missouri", "Indiana", "Iowa", "Vermont",
+                  "Maine", "Maine CD-1", "Maine CD-2")
 
 if (all(analysis_data$state %in% valid_states)) {
   message("Test Passed: The 'state' column contains only valid Australian state names.")
@@ -59,7 +62,7 @@ if (all(analysis_data$state %in% valid_states)) {
 }
 
 # Check if the 'party' column contains only valid party names
-valid_parties <- c("Labor", "Liberal", "Greens", "National", "Other")
+valid_parties <- c("DEM", "REP")
 
 if (all(analysis_data$party %in% valid_parties)) {
   message("Test Passed: The 'party' column contains only valid party names.")

### 2024-11-03 scripts/03-clean_data.R

@@ -17,24 +17,42 @@ president_polls_raw_data <- read.csv('data/01-raw_data/president_polls.csv')
 # 过滤出高质量民调（numeric_grade >= 2.5）的民调
 president_polls_filtered <- president_polls_raw_data %>% 
   janitor::clean_names() %>%
-  select(pollster, numeric_grade, pollscore, methodology, transparency_score, state, 
-         start_date, end_date, sample_size, population, population_full, 
-         hypothetical, party, answer, candidate_name, pct) %>%
+  select(# pollster,
+    numeric_grade,# pollscore,
+         # methodology,
+         # transparency_score,
+         state, 
+         # start_date, 
+         end_date, 
+         sample_size,
+         #population, population_full,
+         # hypothetical,
+         answer, candidate_name, pct) %>%
   tidyr::drop_na()
 
 president_polls_cleaned_data <- president_polls_filtered %>%
   mutate(
-    hypothetical = ifelse(hypothetical == 'true', 1, 0),
+    #hypothetical = ifelse(hypothetical == 'true', 1, 0),
     state = if_else(is.na(state) | state == "", "National", state), 
     end_date = mdy(end_date),
-    start_date = mdy(start_date),
+    #start_date = mdy(start_date),
     num_candidates = round((pct / 100) * sample_size, 0) # 将百分比转换为人数
 ) %>%
   filter(numeric_grade >= 2.5
          , candidate_name %in% c("Kamala Harris", "Donald Trump")
-         , end_date >= as.Date("2024-07-01")
-         , !is.na(end_date))  # 去除缺失的日期
-
+         , end_date >= as.Date("2024-07-21")
+         , !is.na(end_date)  # eliminate date that is null
+) %>%
+  select(# pollster, numeric_grade, pollscore,
+    # methodology,
+    # transparency_score,
+    state, 
+    # start_date, 
+    end_date, 
+    sample_size,
+    #population, population_full, 
+    # hypothetical,
+    answer, candidate_name, pct)
 #### Save data ####
 write_csv(president_polls_cleaned_data, 'data/02-analysis_data/president_polls_cleaned_data.csv')
 #summary(president_polls_cleaned_data)

### 2024-11-03 scripts/example.R

@@ -1,0 +1,228 @@
+#### Set-up ####
+# Load libraries
+library(tidyverse)
+library(janitor)
+library(lubridate)
+library(broom)
+library(modelsummary)
+library(rstanarm)
+library(splines)
+
+
+#### Prepare dataset ####
+# Read in the data and clean variable names
+data <- read_csv("data/01-raw_data/president_polls.csv") |>
+  clean_names()
+
+# Filter data to Harris estimates based on high-quality polls after she declared
+just_harris_high_quality <- data |>
+  filter(
+    candidate_name == "Kamala Harris",
+    numeric_grade >= 2.7 # Need to investigate this choice - come back and fix. 
+    # Also need to look at whether the pollster has multiple polls or just one or two - filter out later
+  ) |>
+  mutate(
+    state = if_else(is.na(state), "National", state), # Hacky fix for national polls - come back and check
+    end_date = mdy(end_date)
+  ) |>
+  filter(end_date >= as.Date("2024-07-21")) |> # When Harris declared
+  mutate(
+    num_harris = round((pct / 100) * sample_size, 0) # Need number not percent for some models
+  )
+
+
+#### Plot data ####
+base_plot <- ggplot(just_harris_high_quality, aes(x = end_date, y = pct)) +
+  theme_classic() +
+  labs(y = "Harris percent", x = "Date")
+
+# Plots poll estimates and overall smoothing
+base_plot +
+  geom_point() +
+  geom_smooth()
+
+# Color by pollster
+# This gets messy - need to add a filter - see line 21
+base_plot +
+  geom_point(aes(color = pollster)) +
+  geom_smooth() +
+  theme(legend.position = "bottom")
+
+# Facet by pollster
+# Make the line 21 issue obvious
+# Also - is there duplication???? Need to go back and check
+base_plot +
+  geom_point() +
+  geom_smooth() +
+  facet_wrap(vars(pollster))
+
+# Color by pollscore
+base_plot +
+  geom_point(aes(color = factor(pollscore))) +
+  geom_smooth() +
+  theme(legend.position = "bottom")
+
+
+#### Starter models ####
+# Model 1: pct as a function of end_date
+model_date <- lm(pct ~ end_date, data = just_harris_high_quality)
+
+# Model 2: pct as a function of end_date and pollster
[…]

### 2024-11-03 paper/paper.qmd
update clean data script

@@
 ```{r}
-# plot graphof pct of two candidates in each state against time
-ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = state)) +
+base_plot <- ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
+  theme_classic() +
+  labs(y = "Candidate Support (%)", x = "Date") 
+#+  scale_x_date(date_labels = "%b %Y")  # 设置 x 轴只显示月份和年份
+
+# 绘制候选人支持率的点图和光滑线
+base_plot + 
+  geom_point() + 
+  geom_smooth(se = FALSE) + 
+  theme(legend.position = "bottom")
+```
+
+```{r}
+# plot graph of pct of two candidates in each state against time
+ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct
+                                         #, color = state
+                                         )
+       ) +
   geom_point() +
@@
   )
-unique(president_polls_cleaned_data$methodology)
 ```

### 2024-11-03 scripts/00-simulate_data.R

@@ -49,8 +49,5 @@ president_polls <- data.frame(
   #, num_candidates = round((pct / 100) * sample_size, 0)
 )
 
-# Check the first few rows of the simulated data
-head(president_polls)
-
 #### Save data ####
 write.csv(president_polls, "data/00-simulated_data/simulated_president_polls.csv")

### 2024-11-03 scripts/03-clean_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw plane data recorded
+# Author: Xinqi Yue
+# Date: 3 Nov 2024
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+# Any other information needed?
 
 #### Workspace setup ####
 library(tidyverse)
@@ -17,56 +17,33 @@ president_polls_raw_data <- read.csv('data/01-raw_data/president_polls.csv')
 # 过滤出高质量民调（numeric_grade >= 2.5）的民调
 president_polls_filtered <- president_polls_raw_data %>% 
   janitor::clean_names() %>%
-  select(# pollster,
-    numeric_grade,# pollscore,
-         # methodology,
-         # transparency_score,
-         state, 
-         # start_date, 
-         end_date, 
-         sample_size,
-         #population, population_full,
-         # hypothetical,
-         answer, candidate_name, pct) %>%
+  select(# pollscore, methodology, transparency_score, start_date, population, population_full, hypothetical, answer, pollster,
+    numeric_grade,
+    state, 
+    end_date, 
+    sample_size,
+    candidate_name, 
+    pct) %>%
   tidyr::drop_na()
 
 president_polls_cleaned_data <- president_polls_filtered %>%
   mutate(
-    #hypothetical = ifelse(hypothetical == 'true', 1, 0),
+    # hypothetical = ifelse(hypothetical == 'true', 1, 0),start_date = mdy(start_date),
     state = if_else(is.na(state) | state == "", "National", state), 
     end_date = mdy(end_date),
-    #start_date = mdy(start_date),
-    num_candidates = round((pct / 100) * sample_size, 0) # 将百分比转换为人数
+    # num_candidates = round((pct / 100) * sample_size, 0)
 ) %>%
   filter(numeric_grade >= 2.5
          , candidate_name %in% c("Kamala Harris", "Donald Trump")
          , end_date >= as.Date("2024-07-21")
[…]

### 2024-11-03 paper/paper.qmd
add simulated data test and analysis data test

@@
 ---
-title: "Prediction of US Election in 2024"
-subtitle: "My subtitle if needed"
+title: "Forecasting the 2024 US Presidential Election"
+subtitle: "A Poll-of-Polls Approach Using Generalized Linear Modeling"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper builds a predictive model to forecast the 2024 US presidential election using a “poll-of-polls” approach, analyzing high-quality polls for Kamala Harris and Donald Trump.
+The model incorporates data on polling methodology, state trends, and candidate support.
+Our findings indicate that xxxxxxxx.
+This study contributes to a deeper understanding of electoral forecasting, helping us interpret aggregated polling data to anticipate election results accurately."
 format: pdf

### 2024-11-03 scripts/00-simulate_data.R

@@ -17,7 +17,7 @@ set.seed(666)
 #### Simulate data ####
 num_rows <- 100  # Number of simulated rows
 
-president_polls <- data.frame(
+simulated_president_polls <- data.frame(
   # pollster = sample(c("Emerson", "YouGov", "Beacon/Shaw", "Quinnipiac", "SurveyUSA", "East Carolina University", "Fairleigh Dickinson", "Ipsos", "Marist", "Siena/NYT", "University of Massachusetts Lowell/YouGov", "Marquette Law School", "Hart/POS", "The Washington Post", "Pew", "Suffolk", "Mason-Dixon",
                       #"Christopher Newport U.", "Data for Progress", "YouGov/Center for Working Class Politics", "UC Berkeley", "Winthrop U.", "High Point University", "McCourtney Institute/YouGov", "Echelon Insights", "CNN/SSRS", "AtlasIntel", "University of Maryland/Washington Post", "Remington", "Muhlenberg", 
                       #"MassINC Polling Group", "U. New Hampshire",  "Siena", "Elon U.", "Selzer", "Data Orbital", "PPIC", "Washington Post/George Mason University", "Kaiser Family Foundation", "SurveyUSA/High Point University", "Roanoke College", "YouGov Blue", "U. North Florida"), num_rows, replace = TRUE),
@@ -43,11 +43,11 @@ president_polls <- data.frame(
                    "Maine", "Maine CD-1", "Maine CD-2"), num_rows, replace = TRUE),  # Random states, including blank for nationwide
   end_date = sample(seq(as.Date("2024-10-16"), as.Date("2024-10-31"), by="day"), num_rows, replace = TRUE),  # Random end dates
   sample_size = sample(400:8000, num_rows, replace = TRUE),  # Random sample sizes between 500 and 3000
-  answer = sample(c("Kamala Harris", "Donald Trump"), num_rows, replace = TRUE),  # Random answers
+  # answer = sample(c("Kamala Harris", "Donald Trump"), num_rows, replace = TRUE),  # Random answers
   candidate_name = sample(c("Kamala Harris", "Donald Trump"), num_rows, replace = TRUE),  # Random candidate names
   pct = round(runif(num_rows, min = 30, max = 60), 1)  # Random percentages between 30 and 60
   #, num_candidates = round((pct / 100) * sample_size, 0)
 )
 
 #### Save data ####
-write.csv(president_polls, "data/00-simulated_data/simulated_president_polls.csv")
[…]

### 2024-11-03 scripts/01-test_simulated_data.R

@@ -1,20 +1,20 @@
 #### Preamble ####
 # Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
+#electoral divisions dataset.
 # Author: Rohan Alexander
 # Date: 26 September 2024
 # Contact: rohan.alexander@utoronto.ca
 # License: MIT
 # Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
+# - The `tidyverse` package must be installed and loaded
+# - 00-simulate_data.R must have been run
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+analysis_data <- read_csv("data/00-simulated_data/simulated_president_polls.csv")
 
 # Test if the data was successfully loaded
 if (exists("analysis_data")) {
@@ -33,19 +33,13 @@ if (nrow(analysis_data) == 100) {
   stop("Test Failed: The dataset does not have 100 rows.")
 }
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
+# Check if the dataset has 6 columns
+if (ncol(analysis_data) == 6) {
+  message("Test Passed: The dataset has 6 columns.")
 } else {
-  stop("Test Failed: The dataset does not have 3 columns.")
+  stop("Test Failed: The dataset does not have 6 columns.")
 }
 
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
-} else {
-  stop("Test Failed: The 'division' column contains duplicate values.")
-}
 
 # Check if the 'state' column contains only valid Australian state names
 valid_states <- c("National", "Arizona", "California", "Georgia", "North Carolina", 
@@ -61,32 +55,47 @@ if (all(analysis_data$state %in% valid_states)) {
   stop("Test Failed: The 'state' column contains invalid state names.")
 }
 
-# Check if the 'party' column contains only valid party names
-valid_parties <- c("DEM", "REP")
 
-if (all(analysis_data$party %in% valid_parties)) {
-  message("Test Passed: The 'party' column contains only valid party names.")
-} else {
-  stop("Test Failed: The 'party' column contains invalid party names.")
-}
-
[…]

### 2024-11-03 scripts/04-test_analysis_data.R

@@ -1,69 +1,73 @@
-#### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+analysis_data <- read_csv("data/02-analysis_data/president_polls_cleaned_data.csv")
 
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
-})
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
-})
+# Check if the dataset has 5 columns
+if (ncol(analysis_data) == 5) {
+  message("Test Passed: The dataset has 5 columns.")
+} else {
+  stop("Test Failed: The dataset does not have 5 columns.")
+}
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
-})
 
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
-})
+# Check if the 'state' column contains only valid Australian state names
+valid_states <- c("National", "Arizona", "California", "Georgia", "North Carolina", 
+                  "Washington", "Pennsylvania", "New Hampshire", "Texas", "Michigan", 
+                  "Nevada", "Wisconsin", "Montana", "Florida", "Ohio", "Massachusetts", "Virginia",
+                  "South Carolina", "Nebraska CD-2", "Minnesota", "New York", "Nebraska", "Maryland",
+                  "New Mexico", "Connecticut", "Rhode Island", "Missouri", "Indiana", "Iowa", "Vermont",
+                  "Maine", "Maine CD-1", "Maine CD-2")
 
-# Test that the 'state' column is character type
-test_that("'state' is character", {
-  expect_type(analysis_data$state, "character")
-})
+if (all(analysis_data$state %in% valid_states)) {
[…]

### 2024-11-03 paper/paper.qmd
update data exploration script add graph in paper

@@
 Each record includes information on the pollster, their grading, polling methodology, transparency score, and specific polling results for each candidate.
+```{r}
+#| label: tbl-raw-data-1
+#| tbl-cap: First 6 entries of Raw Dataset with varibles 'state','end_date','sample_size', 'canadidate_name','pct'
+#| echo: false
+#| warning: false
+#| message: false
+
+raw_data <- read_csv(here::here("data/01-raw_data/president_polls.csv"))
+#Graph
+head_raw_data <- head(raw_data,6)
+# Note there is a type in Description within the original data set itself
+knitr::kable(head_raw_data[, c(13,15,23,51,52)], format = "simple",col.names = c('State','End date','Sample Size', 'Canadidate Name','PCT'))
+
+```
+
+```{r}
+#| label: tbl-analysis-data-1
+#| tbl-cap: First 6 entries of Analysis Dataset
+#| echo: false
+#| warning: false
+#| message: false
+
+#Graph
+head_analysis_data <- head(president_polls_cleaned_data,6)
+# Note there is a type in Description within the original data set itself
+knitr::kable(head_analysis_data[, 1:5], format = "simple", col.names = c('State','End date','Sample Size', 'Canadidate Name','PCT'))
+
+```
 

### 2024-11-03 scripts/05-exploratory_data_analysis.R

@@ -11,27 +11,68 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+library(ggplot2)
+library(ggcorrplot)
 
 #### Read data ####
 analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
+# 读取清理后的数据
+president_polls_cleaned_data <- read.csv('../data/02-analysis_data/president_polls_cleaned_data.csv')
+
+# 描述性统计
+#summary_stats <- 
+president_polls_cleaned_data %>%
+  summarise(
+    avg_pct = mean(pct, na.rm = TRUE),
+    median_pct = median(pct, na.rm = TRUE),
+    min_pct = min(pct, na.rm = TRUE),
+    max_pct = max(pct, na.rm = TRUE),
+    sd_pct = sd(pct, na.rm = TRUE)
   )
+#print(summary_stats)
 
+# 可视化候选人支持率分布
+ggplot(president_polls_cleaned_data, aes(x = candidate_name, y = pct, fill = candidate_name)) +
+  geom_boxplot() +
+  labs(title = "Candidate Support Rate Distribution", y = "Support Rate (%)", x = "Candidate") +
+  theme_minimal()
 
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
+# 时间序列分析
+ggplot(president_polls_cleaned_data, aes(x = as.Date(end_date), y = pct, color = candidate_name)) +
+  geom_line() +
+  labs(title = "Support Rate Trend Over Time", y = "Support Rate (%)", x = "Date") +
+  theme_minimal()
 
+# 相关性分析
+#correlation_matrix <- 
+cor(president_polls_cleaned_data %>% select(pct, sample_size), use = "complete.obs")
+#print(correlation_matrix)
 
+state_support_rates <- president_polls_cleaned_data %>%
+  group_by(state, candidate_name) %>%
[…]

### 2024-11-03 scripts/03-clean_data.R
update data cleaning and model

@@ -11,10 +11,12 @@
 library(tidyverse)
 library(dplyr)
 library(tidyr)
+library(arrow)
+
 #### Clean data ####
 president_polls_raw_data <- read.csv('data/01-raw_data/president_polls.csv')
 
-# 过滤出高质量民调（numeric_grade >= 2.5）的民调
+# filter out high quality polls（numeric_grade >= 2.5)
 president_polls_filtered <- president_polls_raw_data %>% 
   janitor::clean_names() %>%
   select(# pollscore, methodology, transparency_score, start_date, population, population_full, hypothetical, answer, pollster,
@@ -46,4 +48,4 @@ president_polls_cleaned_data <- president_polls_filtered %>%
     pct)
 
 #### Save data ####
-write_csv(president_polls_cleaned_data, 'data/02-analysis_data/president_polls_cleaned_data.csv')
+write_parquet(president_polls_cleaned_data, "data/02-analysis_data/president_polls_cleaned_data.parquet")

### 2024-11-03 scripts/06-model_data.R

@@ -1,13 +1,3 @@
-#### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-
 #### Workspace setup ####
 library(tidyverse)
 library(janitor)
@@ -16,173 +6,110 @@ library(broom)
 library(modelsummary)
 library(rstanarm)
 library(splines)
+library(caret)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+president_polls_cleaned_data <- read_parquet("data/02-analysis_data/president_polls_cleaned_data.parquet")
 
-### Model data ####
-#### 准备数据集 ####
-# 读取数据并清理变量名称
-president_polls_data <- read.csv('data/02-analysis_data/president_polls_cleaned_data.csv')
+#### Construct Model ####
+# Change 'state','candidate_name' to factor variables
 
-#### 初步模型 ####
-# 模型 1：pct 作为 end_date 的函数
-model_date <- lm(pct ~ end_date, data = president_polls_cleaned_data)
+# Set seed for reproducibility
+set.seed(666)
 
-# 模型 2：pct 作为 end_date 和候选人的函数
-model_date_candidates <- lm(pct ~ end_date + candidate_name,
-                            #+ transparency_score + sample_size + numeric_grade + pollscore + num_candidates, 
-                            data = president_polls_cleaned_data)
+# Create a train/test split (80% training, 20% testing)
+train_index <- createDataPartition(president_polls_cleaned_data$pct, 
+                                   p = 0.8, 
+                                   list = FALSE)
 
-# 将模型预测添加到数据中
-president_polls_cleaned_data <- president_polls_cleaned_data |> 
+train_data <- president_polls_cleaned_data[train_index, ]
+test_data <- president_polls_cleaned_data[-train_index, ]
+
+# Change 'state', 'candidate_name' to factor variables in train_data
+train_data <- train_data |> 
   mutate(
-    fitted_date = predict(model_date),
[…]

### 2024-11-03 paper/paper.qmd
update paper content

--- 2024-11-03 paper/paper.qmd
@@
 ```{r}
+#| echo: false
+#| warning: false
+#| message: false
 base_plot <- ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
@@
 ```{r}
+#| echo: false
+#| warning: false
+#| message: false
 # plot graph of pct of two candidates in each state against time
@@
 # Introduction
+The 2024 U.S.
+presidential election is generating significant public interest, with recent polling reflecting shifts in candidate support across various demographic and regional groups.
+Polling data, while insightful, presents challenges due to inherent biases, variability in polling methodology, and regional influences on voter behavior.
+This study aims to address these challenges using a "poll-of-polls" approach, aggregating high-quality national and state polls to forecast voter support for Kamala Harris and Donald Trump.
+By applying Bayesian modeling, this analysis incorporates both the temporal dynamics of candidate support and state-specific trends.
 
-Overview paragraph
-As the United States prepares for the 2024 presidential election, the role of opinion polls in understanding voter preferences remains critical.
-Polls serve as indicators of public sentiment, offering insights into which candidates might have an advantage in the electoral race.
-This paper aims to predict the winner of the upcoming election by analyzing "poll-of-polls" data.
+In this paper, we explore the following questions: How is support for each candidate likely to evolve as the election approaches?
+How do regional differences influence overall voter sentiment?
+This paper contributes to electoral forecasting literature by synthesizing aggregated polling data to provide a nuanced view of candidate support trends.
 
-Estimand paragraph
+# Estimand
+
+Our primary estimand is the percentage of voter support for Donald Trump and Kamala Harris on election day.
+We estimate this support percentage both at the national level and by state, incorporating time and state-specific effects.
 
@@
 
-## Overview
+## Data Overview {#sec-data-overview}
 The dataset encompasses polling data focused on two candidates, Donald Trump and Kamala Harris.
@@
 
-## Explanation of each variables
+The analysis utilizes FiveThirtyEight's dataset of national presidential general election polls [@fivethirtyeight].
+Following the approach outlined in [@tellingstories], we aim to predict the election outcome based on this polling data.
+The analyses were conducted in R @citeR, with support from several packages.
+The `tidyverse` packages [@citetidyverse] were used in the process of data simulation, testing beforehand.
+After the original raw data was downloaded by using `tidyverse` package [@citetidyverse], data cleaning process was done by using `tidyverse` package [@citetidyverse], `lubridate` package [@citelubridate], and `arrow` package [@citearrow].
+Then, models were constructed using `tidyverse` package [@citetidyverse], `lubridate` package [@citelubridate], `rstanarm` [@citerstanarm] package, and `splines` package [@citesplines].
+The model results are then presented by `modelsummary` [@citemodelsummary] package, and graphs were made with `ggplot2` package [@citeggplot].
+
+## Data Clean
+We clean the raw data to produce the analysis dataset using the tools listed in the @sec-data-overview, providing high-quality data for subsequent election analysis.
+Firstly, we standardize column names to lowercase and remove special characters.
+Then, we retain only the fields relevant to the election analysis, such as `state`, `end_date`, `sample_size`, `candidate_name`, and `pct` (percentage support), simplifying the data structure by removing unnecessary columns.
+Next, we remove rows with missing values and replace empty values in the `state` column with "National," indicating these records pertain to nationwide polls.
+Additionally, we convert the `end_date` column to date format, ensuring accuracy in date-based filtering.
+Then, we filter the data to retain only records that meet specific criteria: a `numeric_grade` of 2.5 or higher, a `candidate_name` of either "Kamala Harris" or "Donald Trump" (focusing on these two candidates' support levels), an `end_date` on or after July 21, 2024 (focusing on recent polling when Biden withdrawal from the election), and a non-empty `end_date` (filtering out records with missing dates).
+
+The cleaned data is displayed in @tbl-analysis-data-1, which contains a total of 5 variables:
+```{r}
+#| label: tbl-analysis-data-1
+#| tbl-cap: First 6 entries of Analysis Dataset
+#| echo: false
+#| warning: false
+#| message: false
+
+#Graph
+head_analysis_data <- head(president_polls_cleaned_data,6)
+# Note there is a type in Description within the original data set itself
+knitr::kable(head_analysis_data[, 1:5], format = "simple", col.names = c('State','End date','Sample Size', 'Canadidate Name','PCT'))
+
+```
+
+## Predictors Explanation
+- **state**: The U.S. state where the poll was conducted, which allows for state-by-state analysis and comparison of support levels.
+
+- **end date**: The date the poll concluded, marking the end of data collection for that specific poll.
+
+- **sample size**: The number of respondents in the poll, indicating the scope and potential statistical reliability of the results.
+
+- **candidate_name**: The name of the candidate being polled, which in this data set focuses on Donald Trump and Kamala Harris.
+
+## Outcome Exaplanation
+
+- **pct**: The support percentage each candidate received in the poll, which serves as the outcome variable for analysis.
+
+## Explanation of Other Variables Used
 - **pollster**: The organization that conducted the poll, providing information on who gathered the data.
@@
 
-- **state**: The U.S. state where the poll was conducted, which allows for state-by-state analysis and comparison of support levels.
+## Measurement
+The goal of this measurement is to turn individual voter opinions into a reliable estimate of electoral college outcomes by analyzing polling data.
+This data, sourced from @fivethirty—a trusted platform known for high standards—includes only polls that meet rigorous quality criteria, ensuring broad representation of likely U.S.
+voters.
+Polls provide essential details, such as the pollster’s identity, survey dates, sample size, and methodology, covering data collection mode, demographic weighting, and adjustments to create a representative sample.
+These quality standards, while robust, are based on historical practices, which may overlook recent methodological shifts or emerging biases.
 
-- **start date**: The date the poll began, marking the beginning of data collection for that specific poll.
+## Limitation
+Polling has inherent limitations.
+It provides snapshots of voter sentiment at specific times rather than ongoing updates, potentially missing rapid shifts in public opinion, especially near Election Day.
+Adjustments are made for recency, but participation and response biases—like self-selection and social desirability bias—can still impact accuracy by creating gaps between expressed opinions and actual voting behavior.
+Additionally, regional polling disparities, with battleground states polled more frequently than “safe” states, can lead to imbalances in representation, highlighting the challenge of achieving uniformly accurate forecasts across the nation.
 
-- **end date**: The date the poll concluded, marking the end of data collection for that specific poll.
+## Data visualization
+### Exploring the Relationship Between State and PCT
 
-- **sample size**: The number of respondents in the poll, indicating the scope and potential statistical reliability of the results.
+```{r}
+#| label: fig-pct-state
+#| fig-cap: Support for Candidates by State
+#| echo: false
+#| warning: false
+#| message: false
 
-- **population**: A general description of the population sampled (e.g., likely voters), providing context on who was surveyed.
+# Load ggplot2
+library(ggplot2)
 
-- **population full**: Detailed information about the sample population, offering insights into demographic or eligibility characteristics.
+ggplot(data = president_polls_cleaned_data, aes(x = state, y = pct, fill = candidate_name)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = c("Donald Trump" = "pink", "Kamala Harris" = "lightblue")) + 
+  labs(x = "State",
+       y = "Support Percentage (%)") + # Add X-axis and Y-axis
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
+```
 
-- **hypothetical**: Indicates whether the poll was based on a hypothetical scenario, coded as a binary value.
+### Exploring the Relationship Between End Date and PCT
+```{r}
+#| label: fig-pct-time
+#| fig-cap: Trends in Candidate Support Over Time
+#| echo: false
+#| warning: false
+#| message: false
 
-- **party**: The political party affiliation of the respondent or the focus of the poll, when specified.
+# Load ggplot2
+library(ggplot2)
 
-- **answer**: The poll outcome or response category (e.g., the candidate name or specific answer provided by respondents).
+ggplot(data = president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name, group = candidate_name)) +
+  geom_line(size = 1,alpha = 0.5) + 
+  geom_point(size = 1) + # Add data point
+  scale_color_manual(values = c("Donald Trump" = "pink", "Kamala Harris" = "lightblue")) + 
+  labs(x = "State",
+       y = "Support Percentage (%)") + # Add X-axis and Y-axis
+  theme_minimal() + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-- **candidate_name**: The name of the candidate being polled, which in this data set focuses on Donald Trump and Kamala Harris.
-
-- **pct**: The support percentage each candidate received in the poll, which serves as the outcome variable for analysis.
-
-## Measurement
-Key measurements in the dataset include each poll’s numeric_grade (a quality score for the pollster), pollscore (a specific rating per poll), and transparency_score.
-These indicators help assess and compare the reliability of the included poll results.
-Additionally, records contain information on sample_size, state, start_date, and end_date, capturing the timing and scope of each poll.
-
-## Outcome variables
-The primary outcome variable in this analysis is pct, representing each candidate’s support percentage in individual polls.
-Focusing on support levels for Trump and Harris enables us to evaluate current sentiment and ultimately predict the election outcome.
-
-## Predictor variables
-Predictor variables include pollster, numeric_grade, pollscore, transparency_score, state, sample_size, population, population_full, and methodology.
-These factors provide context for each poll’s results and help assess how factors such as sample size, polling method, and geographical scope may influence support percentages.
+```
 
 # Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+In this analysis, we use a Bayesian linear regression model to estimate the percentage of support (`pct`) for each candidate in the upcoming US presidential election.
+The model includes key predictors such as polling end date (`end_date`), candidate (`candidate_name`), sample size (`sample_size`), and state (`state`).
+Each predictor is selected based on its relevance to the variation in candidate support, as discussed in the data section.
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+In this Bayesian framework, we assume a normal distribution for poll results influenced by several predictors: end date, candidate name, sample size, and state.
+We denote $y_i$ as the percentage of votes for a candidate in a given poll, where $beta_i$ represents the candidate effect, $gamma_i$ reflects the influence of sample size, and $delta_i$ corresponds to the state effect.
+
+The model can be mathematically expressed as follows:
 
 \begin{align}
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+y_i | \mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \\ 
+\mu_i &= \alpha + \beta_1 \cdot \text{end\_date}_i + \beta_2 \cdot \text{candidate\_name}_i + \beta_3 \cdot \text{sample\_size}_i + \sum_{j=1}^{M} \gamma_j \cdot \text{state}_j \\ 
+\alpha &\sim \text{Normal}(50, 10) \\ 
+\beta_1, \beta_2, \beta_3 &\sim \text{Normal}(0, 2.5) \\ 
+\gamma_j &\sim \text{Normal}(0, 2.5) \\ 
+\sigma &\sim \text{Exponential}(1)
 \end{align}
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+In this setup, the intercept $\alpha$ represents the baseline poll result, while each $\beta$ coefficient captures the specific influence of its associated predictor on the vote percentage.
+The variable $\text{state}_j$ accounts for effects attributed to different states, while $\text{end\_date}_{i}$ models temporal trends.
+
+Priors are defined as follows: $alpha$ follows a normal distribution with a mean of 50 and a standard deviation of 10.
+Each of the $\beta$ and $\gamma$ parameters has a normal prior centered at 0 with a standard deviation of 2.5, indicating a mild assumption about their potential effects without introducing bias.
+The noise parameter $\sigma$ adheres to an exponential distribution, facilitating flexibility in the unexplained variation.
+
+We run the model using the @citeR package of @rstanarm, focusing on how the vote percentage varies based on the predictors.
+
+The complete model, summarizing the components, can be expressed as:
+
+$$y_i \sim \text{Normal}\left(\beta_0 + \beta_1 \cdot \text{end\_date}_i + \sum_{k=1}^{K} \gamma_k B_k(\text{state}_j), \sigma^2\right)$$
+
+In this expression, $y_i$ represents the predicted vote percentage for observation $i$, modeled as a function of the predictors, where the mean $\mu_i$ captures the expected percentage, and $\sigma$ reflects the variability.
+
+To further clarify the model:
+
+- **Formula (1)** shows that the response variable $y_i$ is normally distributed, with $\mu_i$ as the expected value and $\sigma$ representing standard deviation.
+- **Formula (2)** illustrates that $\mu_i$ is derived from the intercept $\alpha$ and the predictors.
+- **Formula (3)** details the basis functions applied to the state variable, allowing for a nuanced relationship between states and vote percentages.
+The prior distributions are:
+- **Formula (4)** specifies that $\alpha$ has a normal distribution with mean 50 and variance $10^2$, indicating our expectation of average vote percentage.
+- **Formula (5)** outlines the priors for $\gamma_k$, which are normal distributions centered at 0 with variance $2.5^2$, reflecting the belief in potentially small effects from state variables.
+- **Formula (6)** assigns an exponential distribution to the standard deviation $\sigma$, suggesting that smaller variance is more likely while allowing for broader variations.
+
+## Bayesian Priors
+
+For Bayesian inference, we apply the following prior distributions:
+
+- **Intercept prior**: A `Normal(50, 10)` prior is used for the intercept, reflecting a moderately informative belief that baseline support percentage falls within the plausible range (centered around 50% with a moderate spread).
+- **Coefficients prior**: A `Normal(0, 2.5)` prior is assigned to each regression coefficient, which is weakly informative and allows flexibility without over-restricting the influence of predictors.
+
+These priors are selected to strike a balance between allowing the data to inform estimates while providing regularization to prevent extreme parameter values.
+The priors are justified based on general expectations of support ranges and aim to avoid overfitting.
+
+## Assumptions and Limitations
+
+1.
+**Linearity**: The model assumes a linear relationship between independent variables (predictors) and the dependent variable (outcome, `pct`).
+The expected outcome is represented as a linear combination of the predictors.
+Nonlinear effects, if present, may not be fully captured, potentially affecting the model's fit.
+
+2.
+**Normality of Errors**: It is assumed that the residuals (the differences between observed and predicted values) follow a normal distribution.
+This assumption is crucial for making valid inferences; violations can lead to incorrect conclusions and unreliable credible intervals.
+
+3.
+**Homoscedasticity**: The variance of the residuals is expected to be constant across all combinations of the predictors.
+If residuals display heteroscedasticity (non-constant variance), it can result in inefficient estimates and biased interpretations of the modeled relationships.
+
+4.
+**Independence of Errors**: The model assumes that errors are independent of one another, meaning the error term for any single observation does not affect the error term for another observation.
+However, polling data often includes repeated measures from the same pollster, which may introduce dependence among observations.
+
+5.
+**Additivity**: Predictors are assumed to additively influence `pct`, meaning interactions or non-additive effects are not considered.
+Future versions of the model might benefit from testing interactions, such as between state and candidate.
+
+6.
+**Prior Distributions**: Bayesian regression requires the specification of prior distributions for the model parameters (coefficients).
+The selection of these priors is significant, as they can impact the resulting posterior distributions, particularly when data is limited.
+
+7.
+**Parameter Estimation**: In Bayesian linear regression, parameters are estimated using a posterior distribution derived from both the likelihood of the observed data and the prior distributions.
+This framework allows for uncertainty quantification and more flexible inference.
+
+8.
+**Error Distribution**: The model presumes normally distributed residuals.
+Any deviation from this assumption may influence the validity of the inference.
+Diagnostic checks and posterior predictive checks are used to assess model fit and adherence to assumptions.
+
+## Software and Validation
+
+The model is implemented using the `rstanarm` package in R, which allows for efficient Bayesian inference with automatic convergence diagnostics.
+Model fit and convergence were monitored through trace plots and effective sample sizes.
+To further ensure robustness, we performed posterior predictive checks using `pp_check(model_bayes)` to evaluate model fit and identify any systematic deviations.
+
+Overall, this Bayesian model provides a balanced approach, capturing key effects while maintaining interpretability and flexibility, making it suitable for predicting candidate support percentages in the election context.
 
@@
 
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
 ## Diagnostics
@@
 
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
 \newpage

### 2024-11-03 paper/paper.qmd
update paper

@@
 president_polls_cleaned_data$end_date <- ymd(president_polls_cleaned_data$end_date)
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-base_plot <- ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
-  theme_classic() +
-  labs(y = "Candidate Support (%)", x = "Date") 
-#+  scale_x_date(date_labels = "%b %Y")  # 设置 x 轴只显示月份和年份
-
-# 绘制候选人支持率的点图和光滑线
-base_plot + 
-  geom_point() + 
-  geom_smooth(se = FALSE) + 
-  theme(legend.position = "bottom")
 ```
@@
 ### Exploring the Relationship Between End Date and PCT
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+base_plot <- ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
+  theme_classic() +
+  labs(y = "Candidate Support (%)", x = "Date") 
+#+  scale_x_date(date_labels = "%b %Y")  # 设置 x 轴只显示月份和年份
+
+# 绘制候选人支持率的点图和光滑线
+base_plot + 
+  geom_point() + 
+  geom_smooth(se = FALSE) + 
+  theme(legend.position = "bottom")
+```
+
 ```{r}
@@
 
-## First discussion point {#sec-first-point}
+## Overview of the Paper
+This paper presents a comprehensive analysis of polling data to forecast support for candidates Kamala Harris and Donald Trump in the upcoming U.S.
+presidential election.
+By employing a Bayesian linear regression model, the study investigates how various factors such as polling date, candidate identity, sample size, and geographic location influence voter support.
+The findings contribute to understanding the dynamics of electoral support and the effectiveness of polling methodologies in predicting election outcomes.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Insights About the World
+One significant insight derived from this analysis is the importance of temporal dynamics in voter support.
+The model highlights that the timing of polling can substantially impact the reported support for candidates.
+This finding suggests that voters’ preferences are not static; rather, they fluctuate based on current events, campaign strategies, and media coverage.
+Such insights underscore the need for political strategists and candidates to consider timing when conducting polls and planning campaign efforts.
 
-## Second discussion point
+Another critical takeaway is the varying levels of support for candidates across different states.
+The analysis reveals regional disparities in voter sentiment, indicating that geographic factors significantly influence political preferences.
+This highlights the importance of localized campaign strategies and targeted outreach, as what resonates in one state may not hold true in another.
+Understanding these regional differences can enhance candidates' ability to connect with voters and tailor their messaging effectively.
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+## Limitations of the Study
+Despite its contributions, the study is not without weaknesses.
+One notable limitation is the reliance on existing polling data, which may introduce biases if the data collection methods are not standardized across pollsters.
+Variations in methodology, sample demographics, and question phrasing can lead to discrepancies in reported support levels.
+Additionally, the model assumes a linear relationship between predictors and outcomes, which may oversimplify the complexities of voter behavior.
+A more nuanced approach that incorporates non-linear effects or interactions between variables could provide deeper insights into voter dynamics.
 
-## Third discussion point
+## Future Directions
+Looking ahead, several avenues for further research emerge from this study.
+First, it would be valuable to explore the impact of specific events, such as debates or major news stories, on voter sentiment.
+Incorporating real-time data and sentiment analysis from social media could enrich the understanding of how public opinion shifts in response to external influences.
+Furthermore, expanding the model to include demographic factors—such as age, income, and education—could yield a more comprehensive picture of voter support and the diverse motivations behind electoral choices.
 
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
+In conclusion, while this paper offers valuable insights into electoral dynamics, it also highlights the complexities of voter behavior and the need for continued exploration in this field.
+Future research should strive to incorporate a broader range of variables and methodologies to enhance the predictive accuracy of electoral forecasts and better inform political strategy.
 

### 2024-11-04 paper/paper.qmd
update model script and paper

@@
 ```{r}
-#| echo: false
-#| warning: false
-#| message: false
-base_plot <- ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
-  theme_classic() +
-  labs(y = "Candidate Support (%)", x = "Date") 
-#+  scale_x_date(date_labels = "%b %Y")  # 设置 x 轴只显示月份和年份
-
-# 绘制候选人支持率的点图和光滑线
-base_plot + 
-  geom_point() + 
-  geom_smooth(se = FALSE) + 
-  theme(legend.position = "bottom")
-```
-
-```{r}
 #| label: fig-pct-time
@@
 ggplot(data = president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name, group = candidate_name)) +
-  geom_line(size = 1,alpha = 0.5) + 
+  #geom_line(size = 1,alpha = 0.5) + 
   geom_point(size = 1) + # Add data point
+  geom_smooth(se = FALSE) + 
   scale_color_manual(values = c("Donald Trump" = "pink", "Kamala Harris" = "lightblue")) + 
@@
   theme_minimal() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme(legend.position = "bottom")
 ```
@@
 
-In this Bayesian framework, we assume a normal distribution for poll results influenced by several predictors: end date, candidate name, sample size, and state.
-We denote $y_i$ as the percentage of votes for a candidate in a given poll, where $beta_i$ represents the candidate effect, $gamma_i$ reflects the influence of sample size, and $delta_i$ corresponds to the state effect.
+## Model set-up
+
+In this Bayesian framework, support level are modeled as normally distributed and influenced by several predictors: end date, candidate name, sample size, and state.
+The variable $y_i$ denotes the percentage of votes for a candidate in a specific poll, with $\beta_i$ representing the candidate effect, $\gamma_i$ reflecting the influence of sample size, and $\delta_i$ corresponding to the state effect.
+The intercept $\alpha$ indicates the baseline poll result, while each $\beta_i$ coefficient quantifies the influence of its associated predictor on the vote percentage.
+Additionally, the variable $\text{state}_j$ captures the effects attributed to different states, and $\text{end\_date}_{i}$ models temporal trends.
 
@@
 
-In this setup, the intercept $\alpha$ represents the baseline poll result, while each $\beta$ coefficient captures the specific influence of its associated predictor on the vote percentage.
-The variable $\text{state}_j$ accounts for effects attributed to different states, while $\text{end\_date}_{i}$ models temporal trends.
+Priors are defined as follows.
+For the intercept, a `Normal(50, 10)` distribution is utilized, reflecting a belief that the baseline support percentage is centered around 50% with moderate variability.
+This choice indicates a moderately informative prior that captures plausible ranges for the intercept.
+Each regression coefficient is assigned a `Normal(0, 2.5)` prior, which is weakly informative, allowing flexibility in parameter estimation while minimizing bias.
+These priors are selected to strike a balance between allowing the data to inform estimates and providing regularization to prevent extreme values and overfitting.
+The chosen priors are grounded in reasonable expectations regarding support ranges, aiming to enhance the robustness of the model.
 
-Priors are defined as follows: $alpha$ follows a normal distribution with a mean of 50 and a standard deviation of 10.
-Each of the $\beta$ and $\gamma$ parameters has a normal prior centered at 0 with a standard deviation of 2.5, indicating a mild assumption about their potential effects without introducing bias.
-The noise parameter $\sigma$ adheres to an exponential distribution, facilitating flexibility in the unexplained variation.
+Then, the complete model, summarizing the components, can be expressed as:
 
-We run the model using the @citeR package of @rstanarm, focusing on how the vote percentage varies based on the predictors.
-
-The complete model, summarizing the components, can be expressed as:
-
-$$y_i \sim \text{Normal}\left(\beta_0 + \beta_1 \cdot \text{end\_date}_i + \sum_{k=1}^{K} \gamma_k B_k(\text{state}_j), \sigma^2\right)$$
-
-In this expression, $y_i$ represents the predicted vote percentage for observation $i$, modeled as a function of the predictors, where the mean $\mu_i$ captures the expected percentage, and $\sigma$ reflects the variability.
+$$y_i \sim \text{Normal}\left(\alpha + \beta_1 \cdot \text{end\_date}_i + \beta_2 \cdot \text{candidate\_name}_i + \beta_3 \cdot \text{sample\_size}_i + \sum_{j=1}^{M} \gamma_j \cdot \text{state}_j, \sigma^2\right)$$
 
@@
 
-## Bayesian Priors
-
-For Bayesian inference, we apply the following prior distributions:
-
-- **Intercept prior**: A `Normal(50, 10)` prior is used for the intercept, reflecting a moderately informative belief that baseline support percentage falls within the plausible range (centered around 50% with a moderate spread).
-- **Coefficients prior**: A `Normal(0, 2.5)` prior is assigned to each regression coefficient, which is weakly informative and allows flexibility without over-restricting the influence of predictors.
-
-These priors are selected to strike a balance between allowing the data to inform estimates while providing regularization to prevent extreme parameter values.
-The priors are justified based on general expectations of support ranges and aim to avoid overfitting.
-
-## Assumptions and Limitations
+## Assumptions of the Bayesian Models
 
@@
 This assumption is crucial for making valid inferences; violations can lead to incorrect conclusions and unreliable credible intervals.
+Diagnostic checks and posterior predictive checks are used to assess model fit and adherence to assumptions.
 
@@
 This framework allows for uncertainty quantification and more flexible inference.
-
-8.
-**Error Distribution**: The model presumes normally distributed residuals.
-Any deviation from this assumption may influence the validity of the inference.
-Diagnostic checks and posterior predictive checks are used to assess model fit and adherence to assumptions.
 

### 2024-11-04 scripts/06-model_data.R

@@ -5,6 +5,7 @@ library(lubridate)
 library(broom)
 library(modelsummary)
 library(rstanarm)
+library(arrow)
 library(splines)
 library(caret)
 
@@ -106,10 +107,26 @@ prediction_results <- data.frame(
   predicted_pct = c(mean_predictions_new[1:length(state_names)], mean_predictions_new[(length(state_names)+1):(2*length(state_names))])
 )
 
+# Assuming you have already run the previous code up to the predictions_new part
+
+# Create a dataframe for the predictions with specific columns
+prediction_summary <- data.frame(
+  state = rep(state_names, each = 2),  # Repeat state names for each candidate
+  candidate_name = rep(levels(new_data$candidate_name), times = length(state_names)),
+  predicted_pct = c(mean_predictions_new[1:length(state_names)], 
+                    mean_predictions_new[(length(state_names) + 1):(2 * length(state_names))])
+)
+
+final_results <- prediction_summary |> 
+  select(state, candidate_name, predicted_pct) |>  # Select relevant columns
+  pivot_wider(names_from = candidate_name, values_from = predicted_pct, 
+              names_prefix = "predicted_pct_of_")  # Pivot to wide format
+
+
+
 summary(model_bayes)
 pp_check(model_bayes)
 
 
 # Save model for future use
 saveRDS(model_bayes, "models/election_glm_model.rds")
-

### 2024-11-04 scripts/example.R

@@ -17,7 +17,8 @@ data <- read_csv("data/01-raw_data/president_polls.csv") |>
 # Filter data to Harris estimates based on high-quality polls after she declared
 just_harris_high_quality <- data |>
   filter(
-    candidate_name == "Kamala Harris",
+    candidate_name %in% c("Kamala Harris", "Donald Trump"),
+    #candidate_name == "Kamala Harris",
     numeric_grade >= 2.7 # Need to investigate this choice - come back and fix. 
     # Also need to look at whether the pollster has multiple polls or just one or two - filter out later
   ) |>
@@ -65,7 +66,7 @@ base_plot +
 
 #### Starter models ####
 # Model 1: pct as a function of end_date
-model_date <- lm(pct ~ end_date, data = just_harris_high_quality)
+model_date <- lm(pct ~ end_date + candidate_name, data = just_harris_high_quality)
 
 # Model 2: pct as a function of end_date and pollster
 model_date_pollster <- lm(pct ~ end_date + pollster, data = just_harris_high_quality)
@@ -79,11 +80,19 @@ just_harris_high_quality <- just_harris_high_quality |>
 
 # Plot model predictions
 # Model 1
+ggplot(just_harris_high_quality, aes(x = end_date, color = candidate_name), color = candidate_name) +
+  geom_point(aes(y = pct, color = candidate_name), color = candidate_name) +
+  geom_line(aes(y = fitted_date), color = 'pink', linetype = "dotted") +
+  theme_classic() +
+  labs(y = "Harris percent", x = "Date", title = "Linear Model: pct ~ end_date")
+
+
 ggplot(just_harris_high_quality, aes(x = end_date)) +
   geom_point(aes(y = pct), color = "black") +
   geom_line(aes(y = fitted_date), color = "blue", linetype = "dotted") +
+  facet_wrap(vars(candidate_name)) +
   theme_classic() +
-  labs(y = "Harris percent", x = "Date", title = "Linear Model: pct ~ end_date")
+  labs(y = "Harris percent", x = "Date", title = "Linear Model: pct ~ end_date + pollster")
 
 # Model 2
 ggplot(just_harris_high_quality, aes(x = end_date)) +

### 2024-11-04 paper/paper.qmd
update llm and paper appendix

@@
 title: "Forecasting the 2024 US Presidential Election"
-subtitle: "A Poll-of-Polls Approach Using Generalized Linear Modeling"
+subtitle: "A Poll-of-Polls Approach Using Bayesian Modeling"
 author: 
@@
 date-format: long
-abstract: "This paper builds a predictive model to forecast the 2024 US presidential election using a “poll-of-polls” approach, analyzing high-quality polls for Kamala Harris and Donald Trump.
+abstract: "This paper builds a predictive Bayesian model to forecast the 2024 US presidential election using a “poll-of-polls” approach, analyzing high-quality polls for Kamala Harris and Donald Trump.
 The model incorporates data on polling methodology, state trends, and candidate support.
@@
 
-# Estimand
+## Estimand
 
@@
 The goal of this measurement is to turn individual voter opinions into a reliable estimate of electoral college outcomes by analyzing polling data.
-This data, sourced from @fivethirty—a trusted platform known for high standards—includes only polls that meet rigorous quality criteria, ensuring broad representation of likely U.S.
+This data, sourced from @fivethirtyeight—a trusted platform known for high standards—includes only polls that meet rigorous quality criteria, ensuring broad representation of likely U.S.
 voters.
@@
 Each predictor is selected based on its relevance to the variation in candidate support, as discussed in the data section.
-
-## Model set-up
 
@@
 
+# Methodology Analysis of Texas Politics Project Poll
+
+## Introduction
+This section provides a comprehensive examination of the methodology utilized by YouGov for the October 2024 Texas Statewide Survey, emphasizing the reliability of the organization and its methods, along with a critical analysis of the survey's strengths, weaknesses, and potential improvements.
+
+## Population, Frame, and Sample
+
+- **Population**: The survey aimed to represent Texas registered voters, defined as individuals who meet the eligibility requirements to vote in Texas, including age, residency, and registration status.
+This demographic is critical given the state’s political landscape and upcoming elections.
+
+- **Frame**: The sampling frame is the specific population from which a sample is drawn, constructed from diverse data sources to ensure validity. Key components included:
+  - **American Community Survey (ACS)**: This provides demographic information that reflects the socio-economic characteristics of Texas residents, essential for establishing a representative sampling frame.
+  - **Public voter registration records**: These ensure that the survey captures a valid sample of registered voters, allowing for accurate political representation.
+  - **2020 Current Population Survey (CPS)** and **National Election Pool (NEP) exit polls**: These sources offer insights into voting behaviors and preferences, enriching the sampling frame with relevant context and historical data.
+
+- **Sample Size**: The initial sample comprised 1,338 respondents, which was refined to 1,200 for the final dataset through a process known as matching.
+This process enhances the demographic representativeness of the sample across key characteristics such as gender, age, race, and education.
+
+## Sample Recruitment
+
+- **Recruitment Methods**: YouGov employs a proprietary opt-in survey panel that includes approximately 1.5 million U.S. residents. Key recruitment methods include:
+  - **Web Advertising Campaigns**: Targeted ads based on keyword searches increase the likelihood of engaging relevant respondents, leveraging digital platforms for broad reach.
+  - **Permission-Based Email Campaigns**: This method allows for direct outreach to potential participants who have expressed interest in surveys, ensuring a more willing and engaged respondent pool.
+  - **Telephone-to-Web and Mail-to-Web Recruitment**: These methods broaden the outreach, ensuring access to respondents who may not engage online, thus increasing the overall sample diversity.
+
+- **Diversity and Representation**: The multifaceted recruitment strategy is designed to mitigate biases and enhance the demographic diversity of the panel.
+This is essential for capturing a representative sample in a politically diverse state like Texas.
+
+## Sampling Approach and Trade-offs
+
+- **Two-Stage Sampling Approach**: 
+  1.
+**Target Sample Selection**: A probability sample is drawn from the defined target population, ensuring it accurately reflects the demographic composition of Texas.
+Probability sampling means that each individual in the population has a known, non-zero chance of being selected.
+  2.
+**Matched Sample Selection**: Each target sample member is matched to one or more respondents from the YouGov panel, utilizing a set of variables available in consumer and voter databases.
+Matching involves finding respondents in the panel who share key demographic and behavioral traits with the target sample.
+
+- **Strengths**: This methodology allows for the creation of a sample that closely mirrors the target population’s characteristics, theoretically increasing the external validity of the survey results—external validity refers to the extent to which findings can be generalized to a broader context beyond the study sample.
+
+- **Weaknesses**:
+  - **Non-Random Selection**: The reliance on an opt-in panel introduces potential biases associated with self-selection.
+Respondents who choose to participate may differ significantly from those who do not, potentially affecting the survey's internal validity (the degree to which the survey accurately measures what it intends to measure).
+  - **Matching Limitations**: While proximity matching aims to find the closest respondents, it may not account for all variables that could influence responses, leading to unobserved biases.
+Unobserved biases occur when factors influencing survey responses are not measured or controlled for in the analysis.
+
+## Handling Non-Response
+
+- **Weighting Strategy**: To address non-response bias, YouGov implemented a robust weighting methodology:
+  - **Propensity Score Adjustment**: This involves estimating the likelihood of response based on demographic characteristics, which are then used to weight the matched cases back to the target population.
+Propensity score weighting is a statistical technique that adjusts for differences in observed characteristics between respondents and non-respondents.
+
+- **Challenges**: The success of this strategy hinges on accurate assumptions regarding non-response characteristics, which can be difficult to ascertain.
+If the reasons for non-response are systematically related to the survey topics or demographics, this could undermine the validity of the results, highlighting the importance of addressing potential non-response bias.
+
+## Questionnaire Evaluation
+
+- **Question Design**: The YouGov questionnaire included a series of structured questions aimed at eliciting clear responses regarding voter preferences and opinions on key issues.
+Structured questions are those that offer fixed response options, facilitating easier analysis.
+
+- **Pros**:
+  - **Clarity and Relevance**: Questions were designed to be straightforward, addressing current political concerns likely to engage respondents effectively.
+  - **Comprehensive Coverage**: The questionnaire covered a wide array of topics pertinent to the election, providing rich data for analysis and ensuring relevant insights into voter sentiment.
+
+- **Cons**:
+  - **Length and Complexity**: The extensive nature of the questionnaire could lead to respondent fatigue, increasing the likelihood of incomplete or rushed responses, which may affect data quality.
+Respondent fatigue occurs when participants become tired or disengaged from a survey, leading to lower-quality data.
+  - **Framing and Bias**: The manner in which questions are framed can introduce bias.
+Questions that lack neutral wording may lead to skewed responses based on how they are interpreted by participants, potentially distorting the data collected.
+
+## Recommendations for Improvement
+
+1.
+**Enhanced Recruitment Strategies**: Consider integrating more diverse recruitment channels, such as partnerships with community organizations, to reach underrepresented groups who may not be captured through standard methods.
+
+2. **Improved Matching Techniques**: Exploring advanced statistical techniques or machine learning approaches for matching respondents could enhance the accuracy of the matched sample.
+
+3.
+**Shortening the Questionnaire**: Streamlining the questionnaire to focus on the most critical issues could reduce respondent fatigue and improve engagement, ensuring higher quality data collection.
+
+4.
+**Pilot Testing**: Implementing pilot surveys to test question clarity and structure could help identify potential biases or misunderstandings before full deployment, ensuring that the questions effectively capture the desired information.
+
+5.
+**Transparency in Weighting Methods**: Clearly communicating the assumptions and methods used in weighting would enhance transparency and allow for a more critical evaluation of the findings, fostering trust in the results.
+
+## Conclusion
+
+In summary, YouGov’s methodology for the October 2024 Texas Statewide Survey demonstrates several strengths, particularly in its diverse recruitment strategies and thorough weighting processes.
+However, inherent challenges associated with opt-in panels, matching techniques, and questionnaire design warrant careful consideration.
+By addressing these weaknesses and implementing the suggested improvements, the reliability and validity of future surveys can be enhanced, ultimately providing richer insights into voter behavior and preferences.
+
 # Additional data details

### 2024-11-04 paper/paper.qmd
update reference

@@
 
-# Methodology Analysis of Texas Politics Project Poll
+# Methodology Analysis of Texas Politics Project Poll{#sec-Appendix1}
 
 ## Introduction
-This section provides a comprehensive examination of the methodology utilized by YouGov for the October 2024 Texas Statewide Survey, emphasizing the reliability of the organization and its methods, along with a critical analysis of the survey's strengths, weaknesses, and potential improvements.
+This section provides a examination of the methodology utilized by YouGov for the October 2024 Texas Statewide Survey (@blank2024), stating the reliability of the organization and its methods, along with an analysis of the survey's strengths, weaknesses, and potential improvements.
 
 ## Population, Frame, and Sample
-
 - **Population**: The survey aimed to represent Texas registered voters, defined as individuals who meet the eligibility requirements to vote in Texas, including age, residency, and registration status.
@@
 
+# Appendix: Idealized Methodology and Survey {#sec-Appendix2}
+
+## Objective and Overview
+This survey methodology aims to forecast the U.S.
+presidential election outcome by gathering representative data from a diverse cross-section of American voters.
+The target population includes all eligible U.S.
+voters, spanning a wide array of demographic backgrounds.
+With a budget of $100,000, this methodology employs probability sampling techniques, effective recruitment, and thorough data validation protocols to ensure data accuracy and minimize bias.
+By applying probability sampling, each individual has a known chance of selection, allowing the results to be statistically valid and generalizable.
+This design accounts for demographic, geographic, and political influences, enhancing prediction reliability [@fivethirty; @pewresearch].
+
+### Core Objectives
+- **Representative Sampling**: Achieve a sample reflecting U.S. voting demographics, ensuring insights are applicable to the entire electorate.
+- **Data Quality**: Implement validation processes, including cross-verification, to ensure accuracy.
+- **Statistical Modeling and Aggregation**: Apply statistical models and aggregate polling data to enhance forecast accuracy, as demonstrated in prior election studies.
+
+## Sampling Strategy
+The sampling strategy combines **stratified random sampling** and **quota sampling** for comprehensive representation across key demographics.
+Stratified random sampling ensures each subgroup within the population is represented by dividing the population into strata (e.g., age, gender, race) and sampling randomly within each stratum.
+Quota sampling supplements this by guaranteeing minimum representation across essential demographics.
+
+### Stratification Variables
+- **Age Groups**: 18-29, 30-44, 45-64, 65+
+  - **Gender**: Male, Female, Non-binary/Other
+- **Race/Ethnicity**: White, Black, Hispanic/Latino, Asian, Indigenous, Other
+- **Education Level**: No high school, High school graduate, College graduate, Post-graduate
+- **Income Bracket**: <$30,000, $30,000-$60,000, $60,000-$100,000, >$100,000
+- **Geographic Region**: Northeast, Midwest, South, West
+
+This structure aligns with survey sampling best practices, improving accuracy by ensuring proportional representation [@taherdoost2016sampling; @pewresearch].
+However, balancing stratification variables with cost considerations remains a challenge, as over-stratification can be cost-inefficient.
+
+### Sample Size
+To achieve high accuracy, we will survey **10,000 respondents**, which provides a ±1% margin of error at a 95% confidence level.
+This sample size enables detailed subgroup analyses, such as state or demographic-specific trends, increasing the forecast’s reliability.
+
+### Weighting
+Post-stratification weighting will adjust for any underrepresented or oversampled demographic groups, ensuring the final sample accurately mirrors the voting population [@kalton2003weighting].
+For example, younger voters or minorities will be weighted according to their population proportions.
+
+## Recruitment Strategy
+**Multi-channel outreach** (digital ads, email, and civic organization partnerships) will mitigate non-response bias by ensuring diverse respondent participation.
+This strategy helps correct response imbalances that could distort survey accuracy [@dillman2014internet].
+
+- **Digital Advertisements**: Targeted ads on platforms like Facebook and Instagram to attract diverse demographic groups.
+- **Email Outreach**: Invitations to registered voters via available databases.
+- **Civic Partnerships**: Collaborations with non-profits to enhance diversity and reduce non-response bias.
+- **Incentives**: Participants can enter a lottery for a $100 gift card as motivation.
+
+## Data Validation and Quality Assurance
+Ensuring data integrity is essential for an accurate election forecast. Validation protocols will include:
+
+  - **Captcha Verification**: To prevent bot entries.
+- **Contact Verification**: Confirm email or phone authenticity.
+- **Response Time Monitoring**: Flag unusually quick completions for review.
+- **Voter Registration Check**: If feasible, confirm registration to verify eligibility.
+- **Audits**: Random follow-ups to verify responses.
+
+These measures align with data integrity standards in electoral polling [@pew_survey_methodology].
+
+## Poll Aggregation and Data Analysis
+### Poll Aggregation
+Using a poll-of-polls approach, this survey’s data will combine with data from reputable polling firms (e.g., YouGov, Ipsos), creating a balanced forecast.
+
+- **Weighting by Methodology and Recency**: Polls are weighted based on methodological rigor and recency, favoring recent data.
+- **Bias and Variability Adjustments**: Aggregated data will adjust for any bias among individual polls.
+
+### Modeling Approach
+**Bayesian hierarchical models** will address variability across states, demographics, and regions, enabling both popular vote and Electoral College predictions.
+
+## Budget Allocation
+- **Recruitment and Outreach**: $70,000
+- **Incentives**: $10,000
+- **Survey Platform and Administration**: $5,000
+- **Validation Tools**: $5,000
+- **Analysis Software**: $10,000
+
+## Survey Implementation
+The survey will be conducted through **Google Forms**, providing an accessible, cost-effective platform. Access the survey here: [Google Form Survey](https://forms.gle/sAxVuk3n9gV8e2odA).
+
+### Survey Structure
+
+\begingroup
+\small
+
+**Introduction**: Thank you for participating in our survey to forecast the 2024 U.S. Presidential election outcome. Your responses will remain confidential, and participation is voluntary.
+
+**Section 1: Eligibility Screening**:
+  - U.S. citizenship and voter eligibility questions.
+
+**Section 2: Demographics**:
+  - Questions on age, gender, race, education, income, and region.
+
+**Section 3: Political Views and Voting Intentions**:
+  - Likelihood of voting, party affiliation, candidate choice, and issue importance.
+
+**Section 4: Engagement and Information Sources**:
+  - Questions about primary news sources and engagement with election coverage.
+
+**End Message**: Thank you for your time. For survey inquiries, please contact [duanyi.su@mail.utoronto.ca](mailto:duanyi.su@mail.utoronto.ca).
+
+\endgroup
+
+---
+
+### Design Considerations
+- **Question Wording**: Structured to be clear, neutral, and direct.
+- **Pilot Testing**: A pre-deployment pilot will refine the question flow, ensuring clarity and ease for respondents.
+
+\newpage
 # Additional data details

### 2024-11-04 scripts/example.R
delete unused files and rename some file

@@ -1,237 +1,0 @@
-#### Set-up ####
-# Load libraries
-library(tidyverse)
-library(janitor)
-library(lubridate)
-library(broom)
-library(modelsummary)
-library(rstanarm)
-library(splines)
-
-
-#### Prepare dataset ####
-# Read in the data and clean variable names
-data <- read_csv("data/01-raw_data/president_polls.csv") |>
-  clean_names()
-
-# Filter data to Harris estimates based on high-quality polls after she declared
-just_harris_high_quality <- data |>
-  filter(
-    candidate_name %in% c("Kamala Harris", "Donald Trump"),
-    #candidate_name == "Kamala Harris",
-    numeric_grade >= 2.7 # Need to investigate this choice - come back and fix. 
-    # Also need to look at whether the pollster has multiple polls or just one or two - filter out later
-  ) |>
-  mutate(
-    state = if_else(is.na(state), "National", state), # Hacky fix for national polls - come back and check
-    end_date = mdy(end_date)
-  ) |>
-  filter(end_date >= as.Date("2024-07-21")) |> # When Harris declared
-  mutate(
-    num_harris = round((pct / 100) * sample_size, 0) # Need number not percent for some models
-  )
-
-
-#### Plot data ####
-base_plot <- ggplot(just_harris_high_quality, aes(x = end_date, y = pct)) +
-  theme_classic() +
-  labs(y = "Harris percent", x = "Date")
-
-# Plots poll estimates and overall smoothing
-base_plot +
-  geom_point() +
-  geom_smooth()
-
-# Color by pollster
-# This gets messy - need to add a filter - see line 21
-base_plot +
-  geom_point(aes(color = pollster)) +
-  geom_smooth() +
-  theme(legend.position = "bottom")
-
-# Facet by pollster
-# Make the line 21 issue obvious
-# Also - is there duplication???? Need to go back and check
-base_plot +
-  geom_point() +
-  geom_smooth() +
-  facet_wrap(vars(pollster))
-
-# Color by pollscore
-base_plot +
-  geom_point(aes(color = factor(pollscore))) +
-  geom_smooth() +
-  theme(legend.position = "bottom")
-
-
-#### Starter models ####
-# Model 1: pct as a function of end_date
-model_date <- lm(pct ~ end_date + candidate_name, data = just_harris_high_quality)
-
-# Model 2: pct as a function of end_date and pollster
[…]

### 2024-11-04 scripts/00-simulate_data.R
updata script comments and preamble

@@ -1,13 +1,11 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: simulate data to give first idea
+# Author: Xinqi Yue
+# Date: 3 Nov 2024
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
-
+# Pre-requisites: Null
+# Any other information needed? Null
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -1,14 +1,11 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-#electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated data
+# Author: Xinqi Yue
+# Date: 3 Nov 2024
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-# - The `tidyverse` package must be installed and loaded
-# - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Pre-requisites: simulate data first
+# Any other information needed? Need to have simulated data
 
 
 #### Workspace setup ####

### 2024-11-04 scripts/02-download_data.R

@@ -1,12 +1,11 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from 
-# Author: Rohan Alexander 
-# Date: 1 November 2023
+# Author: Xinqi Yue
+# Date: 3 Nov 2024
 # Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-# Any other information needed? 
-
+# Pre-requisites: Null
+# Any other information needed? Null
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-11-04 scripts/03-clean_data.R

@@ -4,8 +4,8 @@
 # Date: 3 Nov 2024
 # Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-# Any other information needed?
+# Pre-requisites: Null
+# Any other information needed? Null
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-11-04 scripts/04-test_analysis_data.R

@@ -1,3 +1,12 @@
+#### Preamble ####
+# Purpose: Test cleaaned data to ensure validity
+# Author: Xinqi Yue
+# Date: 3 Nov 2024
+# Contact: xinqi.yue@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: download and clean data first
+# Any other information needed? Need to have analysis data/ cleaned data
+
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)

### 2024-11-04 scripts/05-exploratory_data_analysis.R

@@ -1,12 +1,11 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Create exploratory data analysis
+# Author: Xinqi Yue
+# Date: 3 Nov 2024
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: download, clean and test data first
+# Any other information needed? Need to have analysis data
 
 #### Workspace setup ####
 library(tidyverse)
@@ -20,11 +19,10 @@ library(ggcorrplot)
 #### Read data ####
 analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
 
-# 读取清理后的数据
+# read from cleaned data
 president_polls_cleaned_data <- read.csv('../data/02-analysis_data/president_polls_cleaned_data.csv')
 
-# 描述性统计
-#summary_stats <- 
+# summarise data
 president_polls_cleaned_data %>%
   summarise(
     avg_pct = mean(pct, na.rm = TRUE),
@@ -33,31 +31,27 @@ president_polls_cleaned_data %>%
     max_pct = max(pct, na.rm = TRUE),
     sd_pct = sd(pct, na.rm = TRUE)
   )
-#print(summary_stats)
 
-# 可视化候选人支持率分布
+# Visualize the distribution of candidate support
 ggplot(president_polls_cleaned_data, aes(x = candidate_name, y = pct, fill = candidate_name)) +
   geom_boxplot() +
   labs(title = "Candidate Support Rate Distribution", y = "Support Rate (%)", x = "Candidate") +
   theme_minimal()
 
-# 时间序列分析
+# Time Series Analysis
 ggplot(president_polls_cleaned_data, aes(x = as.Date(end_date), y = pct, color = candidate_name)) +
   geom_line() +
   labs(title = "Support Rate Trend Over Time", y = "Support Rate (%)", x = "Date") +
   theme_minimal()
 
-# 相关性分析
-#correlation_matrix <- 
 cor(president_polls_cleaned_data %>% select(pct, sample_size), use = "complete.obs")
[…]

### 2024-11-04 scripts/06-model_data.R

@@ -1,3 +1,12 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from 
+# Author: Xinqi Yue
+# Date: 3 Nov 2024
+# Contact: xinqi.yue@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# Any other information needed?
+
 #### Workspace setup ####
 library(tidyverse)
 library(janitor)

### 2024-11-04 paper/paper.qmd
update data type and preamble

@@
 library(tidyverse)
+library(arrow)
 ```
@@
 # load data
-president_polls_cleaned_data <- read.csv('../data/02-analysis_data/president_polls_cleaned_data.csv')
+president_polls_cleaned_data <- read_parquet('../data/02-analysis_data/president_polls_cleaned_data.parquet')
 # transfer date to standard form

### 2024-11-04 scripts/00-simulate_data.R

@@ -10,6 +10,7 @@
 #### Workspace setup ####
 library(tidyverse)
 library(dplyr)
+library(arrow)
 set.seed(666)
 
 #### Simulate data ####
@@ -48,4 +49,4 @@ simulated_president_polls <- data.frame(
 )
 
 #### Save data ####
-write.csv(simulated_president_polls, "data/00-simulated_data/simulated_president_polls.csv")
+write_parquet(simulated_president_polls, "data/00-simulated_data/simulated_president_polls.parquet")

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -10,8 +10,9 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_president_polls.csv")
+analysis_data <- read_parquet("data/00-simulated_data/simulated_president_polls.parquet")
 
 # Test if the data was successfully loaded
 if (exists("analysis_data")) {

### 2024-11-04 scripts/02-download_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from 
+# Purpose: Downloads and saves the data from 538 abcNews
 # Author: Xinqi Yue
 # Date: 3 Nov 2024
 # Contact: xinqi.yue@mail.utoronto.ca
@@ -9,8 +9,8 @@
 
 #### Workspace setup ####
 library(tidyverse)
-president_polls_raw_data <- read.csv('data/01-raw_data/president_polls.csv')
 
+president_polls_raw_data <- read_csv("https://projects.fivethirtyeight.com/polls/data/president_polls.csv")
 #### Save data ####
 # change the_raw_data to whatever name you assigned when you downloaded it.
-# write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+write_parquet(president_polls_raw_data, "data/01-raw_data/president_polls.parquet")

### 2024-11-04 scripts/03-clean_data.R

@@ -14,7 +14,7 @@ library(tidyr)
 library(arrow)
 
 #### Clean data ####
-president_polls_raw_data <- read.csv('data/01-raw_data/president_polls.csv')
+president_polls_raw_data <- read_parquet('data/01-raw_data/president_polls.parquet')
 
 # filter out high quality polls（numeric_grade >= 2.5)
 president_polls_filtered <- president_polls_raw_data %>% 

### 2024-11-04 scripts/04-test_analysis_data.R

@@ -10,8 +10,9 @@
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
+library(arrow)
 
-analysis_data <- read_csv("data/02-analysis_data/president_polls_cleaned_data.csv")
+analysis_data <- read_parquet("data/02-analysis_data/president_polls_cleaned_data.parquet")
 
 
 #### Test data ####

### 2024-11-04 scripts/06-model_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from 
+# Purpose: Create predictive Bayesian Modeling
 # Author: Xinqi Yue
 # Date: 3 Nov 2024
 # Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-# Any other information needed?
+# Pre-requisites: Null
+# Any other information needed? Null
 
 #### Workspace setup ####
 library(tidyverse)
@@ -106,12 +106,12 @@ predictions_new <- posterior_predict(model_bayes, newdata = new_data)
 # Calculate mean predictions for new data
 mean_predictions_new <- colMeans(predictions_new)
 
-# 创建一个数据框，包含州、候选人名称和对应的平均预测值
+# Create a data frame containing the states, candidate names, and corresponding average predictions
 state_names <- levels(new_data$state)
 
-# 准备结果数据框
+# Prepare the result dataframe
 prediction_results <- data.frame(
-  state = rep(state_names, each = 2),  # 每个州两次，分别对应两个候选人
+  state = rep(state_names, each = 2),  # Twice in each state, one for each candidate
   candidate_name = rep(levels(new_data$candidate_name), times = length(state_names)),
   predicted_pct = c(mean_predictions_new[1:length(state_names)], mean_predictions_new[(length(state_names)+1):(2*length(state_names))])
 )
@@ -131,11 +131,8 @@ final_results <- prediction_summary |>
   pivot_wider(names_from = candidate_name, values_from = predicted_pct, 
               names_prefix = "predicted_pct_of_")  # Pivot to wide format
 
-
-
 summary(model_bayes)
 pp_check(model_bayes)
-
 
 # Save model for future use
 saveRDS(model_bayes, "models/election_glm_model.rds")

### 2024-11-04 paper/paper.qmd
ujpdate appendix 2

@@
 The model results are then presented by `modelsummary` [@citemodelsummary] package, and graphs were made with `ggplot2` package [@citeggplot].
+
+```{r}
+#| label: fig-all-obs
+#| tbl-cap: Support Rates of Donald Trump and Kamala Harris by State
+#| echo: false
+#| warning: false
+#| message: false
+state_support_rates <- president_polls_cleaned_data %>%
+  group_by(state, candidate_name) %>%
+  summarise(avg_pct = mean(pct, na.rm = TRUE)) %>%
+  ungroup()
+
+# Correlation analysis
+ggplot(state_support_rates, aes(x = state, y = avg_pct, fill = candidate_name)) +
+  geom_bar(stat = "identity", position = "dodge", width = ) +
+  labs(title = "Support Rates of Donald Trump and Kamala Harris by State",
+       y = "Average Support Rate (%)",
+       x = "State") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
+  geom_point(size = 0.5) +
+  facet_wrap(~ state, scales = "free_y") +
+  labs(title = "Support Rates of Donald Trump and Kamala Harris by State",
+       y = "Support Rate (%)",
+       x = "Date",
+       color = "Candidate") +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
 
@@
 
-\begingroup
-\small
+**Title:**
 
-**Introduction**: Thank you for participating in our survey to forecast the 2024 U.S. Presidential election outcome. Your responses will remain confidential, and participation is voluntary.
+  2024 U.S. Presidential Election Forecast Survey
 
-**Section 1: Eligibility Screening**:
-  - U.S. citizenship and voter eligibility questions.
+**Introduction:**
 
-**Section 2: Demographics**:
-  - Questions on age, gender, race, education, income, and region.
+  We appreciate your participation in this survey, which aims to forecast the outcome of the 2024 U.S. Presidential election. Your responses are essential for our research.
 
-**Section 3: Political Views and Voting Intentions**:
-  - Likelihood of voting, party affiliation, candidate choice, and issue importance.
+**Please note:**
 
-**Section 4: Engagement and Information Sources**:
-  - Questions about primary news sources and engagement with election coverage.
+  - Your answers will be treated with complete confidentiality.
 
-**End Message**: Thank you for your time. For survey inquiries, please contact [duanyi.su@mail.utoronto.ca](mailto:duanyi.su@mail.utoronto.ca).
+- Participation in this survey is voluntary.
+
+- We encourage you to provide honest and thoughtful responses.
+
+- The survey is estimated to take about 5 minutes to complete.
+
+- If you have any questions or concerns, feel free to reach out to our research team at [duanyi.su@mail.utoronto.ca](duanyi.su@mail.utoronto.ca) (Xinqi Yue, Yawen Tan, Duanyi Su).
+
+Thank you for your valuable contribution! As a token of our appreciation, each participant will receive $5 upon completion of the survey.
+
+**Section 1: About Eligibility**
+
+  Are you a U.S. citizen?
+
+  - Yes
+
+- No (Please end Survey)
+
+Do you meet your state’s residency requirements?
+
+  - Yes
+
+- No (Please end Survey)
+
+Will you be 18 years old  or elder by the Election Day?
+
+  - Yes
+
+- No (Please end Survey)
+
+Are you registered to vote by the voter registration deadline. (North Dakota does not require voter registration.)
+
+- Yes
+
+- No
+
+- Wish to register later
+
+**Section 2: About Demographics**
+
+The following questions will help us understand the background characteristics of our respondents.
+
+Which age group do you belong to?
+
+- 18-29
+
+- 30-44
+
+- 45-64
+
+- 65 or older
+
+What is your gender?
+- Male
+
+- Female
+
+- Prefer not to say
+
+- Other
+
+What is your race or ethnicity? Please select all that apply.
+- White
+
+- Black or African American
+
+- Hispanic or Latino
+
+- Asian
+
+- Native American or Alaska Native
+
+- Native Hawaiian or Other Pacific Islander
+
+- Prefer not to say
+
+- Other
+
+Which U.S. state do you currently live in?
+
+[answer box]
+
+What region do you live in within your state?
+
+- Rural
+
+- Suburban
+
+- Urban
+
+- Prefer not to say
+
+What is your political affiliation?
+
+- Democratic
+
+- Republican
+
+- Independent
+
+- Libertarian
+
+- Green Party
+
+- Prefer not to say
+
+- Other
+
+**Section 3: Voting Behavior and Intentions**
+
+These questions focus on voting registration and plans for the upcoming election.
+
+How likely is it that you will vote in the 2024 U.S. Presidential Election?
+
+- Very likely
+
+- Somewhat likely
+
+- Somewhat unlikely
+
+- Very unlikely
+
+If the election were held today, which candidate would you most likely vote for?
+
+- Donald Trump
+
+- Kamala Harris
+
+- Not sure
+
+- Prefer not to say
+
+- Other
+
+How confident are you that your choice would remain the same by Election Day?
+
+- Not at all confident
+
+- Slightly confident
+
+- Moderately confident
+
+- Very confident
+
+- Completely confident
+
+**Section 4: Engagement with the Election**
+
+This section aims to understand how actively our respondents follow and discuss the election.
+
+How closely do you follow news and updates related to the 2024 U.S. Presidential Election?
+
+- Very closely
+
+- Somewhat closely
+
+- Not very closely
+
+- Not at all
+
+How often do you discuss the 2024 U.S. Presidential Election with friends, family, or colleagues?
+
+- Daily
+
+- Weekly
+
+- Occasionally
+
+- Rarely
+
+- Never
+
+**Section 5: Additional Insights**
+
+We appreciate any additional thoughts our respondents may have on the upcoming election.
+
+Do you have any further comments or insights about the factors that might affect the 2024 U.S. Presidential Election? (optional)
+
+[Answer box]
+
+**End Message:**
+
+Thank You for Completing the Survey!
+
+We appreciate your time and thoughtful responses.
+Your participation is invaluable in helping us gather insights for our research on the 2024 U.S.
+Presidential Election forecast.
+Your answers will contribute to a more comprehensive understanding of voter trends and factors influencing this election.
+
+If you have any further questions or would like to know more about this study, please feel free to reach out to our research team at [anjojoo.xu@mail.utoronto.ca](anjojoo.xu@mail.utoronto.ca).
+
+As a thank you, each participant will receive a $5 reward shortly after survey completion.
 
@@
 \newpage
+
 # Additional data details

### 2024-11-04 paper/paper.qmd
update intro, discussion, result in qmd

@@
 The model incorporates data on polling methodology, state trends, and candidate support.
-Our findings indicate that xxxxxxxx.
-This study contributes to a deeper understanding of electoral forecasting, helping us interpret aggregated polling data to anticipate election results accurately."
+Our findings indicate that although no candidate is guaranteed to win a total of 270 electoral votes due to lack of polls in certain states, Kamala Harris is more likely to win the election with 222 electoral votes against Donald Trump's 109 electoral votes.
+This study contributes to an understanding of electoral forecasting, helping us interpret aggregated polling data to anticipate election results."
 format: pdf
 number-sections: true
+table-of-contents: true
+toc-depth: 2
 bibliography: references.bib
@@
 #| message: false
-
+library(dplyr)
+library(tidyr)
+library(knitr)
+library(rstanarm)
+library(ggplot2)
 library(tidyverse)
@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-# plot graph of pct of two candidates in each state against time
-ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct
-                                         #, color = state
-                                         )
-       ) +
-  geom_point() +
-  facet_wrap(~ candidate_name, scales = "free_y") +
-  theme_minimal() +
-  #theme(legend.position = "bottom") +
-  labs(
-    y = "pct",
-    x = "end date",
-    color = "state",
-    title = "pct of Donald Trump and Kamala Harris in each states",
-  )
-```
-
 # Introduction
@@
 
-In this paper, we explore the following questions: How is support for each candidate likely to evolve as the election approaches?
-How do regional differences influence overall voter sentiment?
-This paper contributes to electoral forecasting literature by synthesizing aggregated polling data to provide a nuanced view of candidate support trends.
+Our model predicts trends in voter support for the 2024 U.S.
+Presidential Election, focusing on Donald Trump and Kamala Harris.
+The results, visualized in @fig-modelvisual, indicate stable support for Harris at an estimated 52% nationally, with a confidence interval of approximately 49% to 55%.
+Trump’s predicted support level centers around 46%, with a range of about 43% to 49%, showing a slight downward trend as the election date nears.
+State-specific polling results highlight variances, with Harris showing stronger support in traditionally Democratic areas like Maine CD-1, where predicted support reaches around 62%.
+In contrast, battleground states such as Georgia, Florida, and Pennsylvania exhibit closely contested support levels, reflecting competitive races in these regions.
+These predictions underscore the variability in voter sentiment across states, illustrating the importance of both national and regional factors shaping the electoral landscape.
+
+In remainder of this paper, we structure our analysis as follows.
+@sec-data provides a detailed overview of the data used, including the data cleaning process, explanations of the predictor and outcome variables, as well as other variables that contribute to the model.
+We also present relevant data visualizations to illustrate initial trends and patterns.
+@sec-model focuses on the model setup and methodology, specifically detailing the Bayesian model used, its underlying assumptions, and software choices.
+@sec-result presents our main results, including both the model's outputs and the predictions of voter support for the key candidates.
+In @sec-discussion, we discuss the findings, offer insights into the broader implications, and highlight the limitations and potential directions for future research.
+Finally, the appendices provide additional methodological analysis, an idealized survey methodology, and supporting details for the data and model diagnostics.
 
@@
 
-Results paragraph
-
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
-
 # Data {#sec-data}
@@
 ## Data Overview {#sec-data-overview}
-The dataset encompasses polling data focused on two candidates, Donald Trump and Kamala Harris.
-Data has been filtered to include only results from pollsters with a numeric grade above 2.5 to maintain quality and consistency.
-This selection allows us to focus on higher-rated sources, which may enhance the reliability of predictions.
-Each record includes information on the pollster, their grading, polling methodology, transparency score, and specific polling results for each candidate.
+@sec-data centers on a polling dataset for Donald Trump and Kamala Harris, filtered for quality by including only results from pollsters with a numeric grade above 2.5.
+Key variables such as state, end date, sample size, candidate name, and support percentage (pct) are identified.
+The data cleaning process standardizes column names, retains relevant fields, and addresses missing values to ensure high-quality data for analysis.
+The section includes a table presenting the first six entries of the cleaned analysis dataset, alongside multiple graphs: a bar graph comparing candidate support percentages by state, scatter plots illustrating trends in candidate support over time, and visualizations examining the relationship between sample size and support percentages.
 
@@
 The model results are then presented by `modelsummary` [@citemodelsummary] package, and graphs were made with `ggplot2` package [@citeggplot].
-
-```{r}
-#| label: fig-all-obs
-#| tbl-cap: Support Rates of Donald Trump and Kamala Harris by State
-#| echo: false
-#| warning: false
-#| message: false
-state_support_rates <- president_polls_cleaned_data %>%
-  group_by(state, candidate_name) %>%
-  summarise(avg_pct = mean(pct, na.rm = TRUE)) %>%
-  ungroup()
-
-# Correlation analysis
-ggplot(state_support_rates, aes(x = state, y = avg_pct, fill = candidate_name)) +
-  geom_bar(stat = "identity", position = "dodge", width = ) +
-  labs(title = "Support Rates of Donald Trump and Kamala Harris by State",
-       y = "Average Support Rate (%)",
-       x = "State") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
-  geom_point(size = 0.5) +
-  facet_wrap(~ state, scales = "free_y") +
-  labs(title = "Support Rates of Donald Trump and Kamala Harris by State",
-       y = "Support Rate (%)",
-       x = "Date",
-       color = "Candidate") +
-  theme_minimal() +
-  theme(legend.position = "bottom")
-```
 
@@
 
+pct is the support percentage each candidate received in the poll, which serves as the outcome variable for analysis.
+This variable is crucial for understanding the electoral dynamics, as it quantifies the level of public backing for each candidate at a given time and place.
+By analyzing the pct variable, researchers can assess trends in voter sentiment, compare the effectiveness of campaign strategies, and identify which demographic groups are more inclined to support one candidate over the other.
+Additionally, fluctuations in the pct can signal shifts in public opinion that may correlate with significant political events, media coverage, or changes in candidates' messaging.
+This outcome variable allows for a comprehensive analysis of the electoral landscape, providing insights into how various factors influence voter behavior and preferences throughout the campaign.
+
 ## Explanation of Other Variables Used
@@
 These quality standards, while robust, are based on historical practices, which may overlook recent methodological shifts or emerging biases.
-
-## Limitation
 Polling has inherent limitations.
@@
 #| message: false
-
-# Load ggplot2
-library(ggplot2)
+#| fig-width: 14
+#| fig-height: 8
 
@@
 ```
+@fig-pct-state compares support percentages for Donald Trump and Kamala Harris across U.S.
+states, using pink bars for Trump and light blue for Harris.
+The y-axis shows support percentages up to around 70%, while the x-axis lists states, each with two bars per candidate.
+@fig-pct-state reveals regional popularity variations.
+In some states, bars for both candidates are nearly equal in height, indicating competitive support.
+Other states show one candidate with a clear lead, highlights the varying levels of popularity for each candidate in different regions, which may reflect political, demographic, or regional factors influencing voter preferences.
+For instance, California leans toward Harris, with a taller blue bar, while Texas favors Trump, with a taller pink bar.
+These patterns reflect regional political tendencies, suggesting which states might be strongholds or battlegrounds.
+They highlight potential areas where each candidate could focus efforts to strengthen support or appeal to undecided voters.
 
@@
 #| message: false
+#| fig-width: 7
+#| fig-height: 3
 
@@
   scale_color_manual(values = c("Donald Trump" = "pink", "Kamala Harris" = "lightblue")) + 
-  labs(x = "State",
-       y = "Support Percentage (%)") + # Add X-axis and Y-axis
+  labs(x = "End Date",
+       y = "Support Percentage (%)",
+       color = "Candidate Name") +
   theme_minimal() + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  #theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
   theme(legend.position = "bottom")
@@
 
-# Model
+@fig-pct-time visualizes support percentages for Donald Trump and Kamala Harris over time, with each point representing a poll.
+The x-axis shows poll end dates, extending beyond July 21st, while the y-axis reflects support percentages.
+Pink dots represent Trump, and light blue dots represent Harris.nTrend lines for each candidate show Harris consistently above Trump, indicating a slight but steady lead.
+Harris’s trend remains around 50%, while Trump’s is just below.
+Both lines are stable, with no major fluctuations in support over time, suggesting limited change in public opinion.
+The close clustering of points around each trend line indicates steady support levels for both candidates, with Harris maintaining a modest lead throughout the period.
+
+```{r}
+#| label: fig-pct-sample-size
+#| fig-cap: Support for Candidates by Sample Size
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 7
+#| fig-height: 3
+
+# Load ggplot2
+library(ggplot2)
+
+ggplot(data = president_polls_cleaned_data, aes(x = sample_size, y = pct, color = candidate_name, group = candidate_name)) +
+  geom_point(size = 1) + # Add data point
+  scale_color_manual(values = c("Donald Trump" = "pink", "Kamala Harris" = "lightblue")) + 
+  labs(x = "Sample size",
+       y = "Support Percentage (%)",
+       color = "Candidate Name") + 
+  theme_minimal() + 
+  #theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme(legend.position = "bottom")
+```
+@fig-pct-sample-size examines the relationship between poll sample size and support percentage for Donald Trump and Kamala Harris.
+The x-axis represents poll sample sizes, ranging from a few hundred to over 6,000, while the y-axis shows support percentages.
+Pink dots indicate Trump’s support, and light blue dots represent Harris.
+Most polls have sample sizes under 2,000, with support percentages clustering between 40% and 55% for both candidates.
+As sample sizes increase, support percentages stabilize around the 45%–55% range, though fewer large-sample polls exist.
+Smaller polls show more variability, with support percentages ranging from 30% to 60%, while larger polls yield more consistent results near 50%.Overall, the plot suggests that larger polls offer more stable estimates of support, while smaller polls tend to show greater fluctuation.
+
+### Exploring the Relationship Between End Date and State and PCT
+```{r}
+#| label: fig-all-obs
+#| fig-cap: Support Rates of Donald Trump and Kamala Harris by State and end date
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 8
+#| fig-height: 10
+
+state_support_rates <- president_polls_cleaned_data %>%
+  group_by(state, candidate_name) %>%
+  summarise(avg_pct = mean(pct, na.rm = TRUE)) %>%
+  ungroup()
+
+ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
+  geom_point(size = 0.7) +
+  facet_wrap(~ state, scales = "free_y") +
+  labs(title = "Support Rates of Donald Trump and Kamala Harris by State",
+       y = "Support Rate (%)",
+       x = "Date",
+       color = "Candidate Name") +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+```
+@fig-all-obs comprises scatter plots illustrating the support rates for Donald Trump and Kamala Harris across various states, with the y-axis representing percentage support and the x-axis indicating the timeline.
+Red dots represent Trump's support, while blue dots indicate Harris's.
+The visualization shows fluctuating support levels for both candidates, with Harris generally receiving higher support in states like California and New York, whereas states like Florida and Indiana display a more competitive landscape.
+The national plot reveals trends in support, reflecting periods of gain or loss for both candidates, suggesting that voter sentiment is dynamic and influenced by external factors during the campaign.
+Overall, the figure highlights the changing electoral support for Trump and Harris across states and time.
+
+# Model {#sec-model}
 In this analysis, we use a Bayesian linear regression model to estimate the percentage of support (`pct`) for each candidate in the upcoming US presidential election.
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+In this analysis, we utilize a Bayesian linear regression model to predict the percentage of voter support for Donald Trump and Kamala Harris in the 2024 U.S.
+Presidential Election.
+This choice of modeling framework is particularly suitable for our objectives, as it allows for the incorporation of prior knowledge regarding electoral dynamics while updating predictions based on newly observed data.
+The Bayesian approach provides a robust mechanism for estimating uncertainty in our predictions, which is crucial in the context of political polling where public sentiment can fluctuate significantly.
+The model structure includes key predictors: the polling end date, candidate name, sample size, and state.
+The use of these predictors is justified by their established relevance in previous electoral analyses, highlighting their roles in shaping voter preferences.
+The inclusion of `end_date` facilitates the examination of temporal trends in support, reflecting how candidate visibility and public sentiment evolve as the election date approaches.
+We model the outcome variable, support percentage (pct), as a normally distributed random variable influenced by these predictors.
+The mathematical formulation allows for the representation of the intercept, which denotes the baseline support level, alongside coefficients that quantify the influence of each predictor.
+The priors assigned to the model parameters are carefully chosen to reflect reasonable expectations based on historical voting patterns, thus enhancing the model's interpretability and effectiveness.
+Moreover, the Bayesian framework enables the modeling of potential interactions between state-specific effects and candidate support, allowing us to capture the regional variations that are often observed in electoral outcomes.
+By incorporating individual pollster effects as fixed coefficients, we can account for the inherent biases associated with different polling organizations, ensuring that our model provides a nuanced view of candidate support.
+This model's formulation strikes a balance between complexity and interpretability, allowing for a comprehensive analysis of the factors influencing voter sentiment while maintaining computational efficiency.
+The Bayesian approach not only enhances our understanding of electoral dynamics but also provides a statistically sound basis for forecasting potential election outcomes.
+Overall, the chosen model is well-aligned with the objectives of this study, facilitating a robust analysis of polling data to derive meaningful insights into the upcoming election.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+# Results {#sec-result}
 
-# Results
-
-Our results are summarized in @tbl-modelresults.
+## Model Result
 
@@
 
-library(rstanarm)
+model<-
+  readRDS(file = here::here("models/election_glm_model.rds"))
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| tbl-cap: "Model Results of Trump Percentage Vote based on Date and State"
 #| warning: false
@@
   list(
-    "First model" = first_model
+    "Bayesian Model" = model
   ),
-  statistic = "mad",
   fmt = 2
@@
 
-# Discussion
+@tbl-modelresults provide insights into the factors influencing voter support for Donald Trump and Kamala Harris, based on a total of 846 observations.
+The model intercept is estimated at -397.72, serving as a baseline from which other coefficients are interpreted.
+Notably, the coefficient for the polling end date is 0.02, indicating a positive relationship between the date and support percentage, suggesting that as the election approaches, support for the candidates slightly increases, likely due to heightened visibility and engagement.
+The coefficient for Kamala Harris is 1.81, reflecting her higher expected support relative to Donald Trump, which indicates her appeal among voters during the polling period.
+@tbl-modelresults also includes state-specific coefficients that capture regional variations in support.
+For instance, states such as Maine CD-1 (4.05), Missouri (1.66), and New Mexico (1.73) show positive coefficients, indicating stronger support for the candidate in these regions.
+Conversely, negative coefficients for states like Vermont (-2.37), New York (-1.92), and Massachusetts (-1.85) suggest lower support levels, highlighting potential challenges in these areas.
+However, the model's adjusted R² value of -0.056 indicates that the predictors included do not explain a substantial amount of the variability in support percentages, suggesting that other unmeasured factors may influence voter preferences.
+The log-likelihood value of -2412.946, along with an effective sample size for the expected log pointwise predictive density (ELPD) of -2463.8 and a leave-one-out information criterion (LOOIC) of 4927.6, indicate moderate predictive accuracy.
+Additionally, the root mean square error (RMSE) of 4.18 suggests that the predicted percentages deviate from actual support levels by approximately 4.18 percentage points on average.
+Overall, these results underscore the importance of both temporal dynamics and regional differences in predicting voter support, while also indicating a need for further exploration of additional variables that may more effectively account for observed voter preferences.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: fig-modelvisual
+#| fig-cap: "Predict Posterior Draws and Spline Fit for Vote Percentage"
+#| warning: false
+#| fig-width: 12
+#| fig-height: 8
+
+# Create a new data frame for predictions
+new_data <- expand.grid(
+  end_date = seq(
+    min(president_polls_cleaned_data$end_date),
+    max(president_polls_cleaned_data$end_date),
+    length.out = 100
+  ),
+  sample_size = mean(president_polls_cleaned_data$sample_size),
+  state = factor(c("National", "Arizona", "California", "Georgia", "North Carolina", "Washington", "Pennsylvania", "New Hampshire", "Texas", "Michigan", "Nevada", "Wisconsin", "Montana", "Florida", "Ohio", "Massachusetts", "Virginia", "South Carolina", "Nebraska CD-2", "Minnesota", "New York", "Nebraska", "Maryland", "New Mexico", "Connecticut", "Rhode Island", "Missouri", "Indiana", "Iowa", "Vermont", "Maine", "Maine CD-1", "Maine CD-2")),
+  candidate_name = factor(c("Kamala Harris", "Donald Trump"))  # Only two candidates for simplicity
+)
+
+# Generate posterior predictions
+posterior_preds <- posterior_predict(model, newdata = new_data)
+
+# Summarize predictions
+pred_summary <- new_data %>%
+  mutate(
+    pred_mean = colMeans(posterior_preds),
+    pred_lower = apply(posterior_preds, 2, quantile, probs = 0.025),
+    pred_upper = apply(posterior_preds, 2, quantile, probs = 0.975)
+  )
+
+# Visualization
+ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
+  geom_point(aes(shape = state), alpha = 0.5) +  # Use state as shape
+  geom_line(
+    data = pred_summary,
+    aes(x = end_date, y = pred_mean, color = candidate_name),
+    size = 1.2,  # Make the line thicker
+    inherit.aes = FALSE
+  ) +
+  geom_ribbon(
+    data = pred_summary,
+    aes(x = end_date, ymin = pred_lower, ymax = pred_upper),
+    alpha = 0.2,
+    inherit.aes = FALSE
+  ) +
+  labs(
+    x = "End Date",
+    y = "Percentage",
+    title = "Predicted Percentage Over Time",
+    color = "Candidate",
+    shape = "State"
+  ) +
+  theme_minimal() +
+  theme(
+    legend.key.size = unit(1, "cm"),
+    legend.text = element_text(size = 8) 
+  )
+
+```
+@fig-modelvisual produced predicted percentages of voter support for Donald Trump and Kamala Harris over time, as shown in the graph titled "Predicted Percentage Over Time." The y-axis represents the predicted support percentage, while the x-axis indicates polling end dates.
+@fig-modelvisual reveals distinct trends in voter support for both candidates.
+The predictions for Kamala Harris (shown in teal) suggest a mean support level consistently around 52% during this period, with the confidence interval shaded in gray indicating a range from approximately 49% to 55%.
+This stability suggests that Harris maintains a competitive edge in voter support as the election date approaches.In contrast, the predicted percentages for Donald Trump (shown in red) indicate a mean support level around 46%, with a confidence interval ranging from about 43% to 49%.
+This pattern highlights a slight downward trend in Trump’s predicted support, suggesting potential challenges in consolidating voter sentiment as the election draws near.
+The individual data points on the graph represent specific state polling results, with various shapes indicating different states.
+For example, Maine CD-1 stands out with a higher predicted support for Harris at approximately 62%, which is significantly above the national average, indicating a strong preference in this district.
+Conversely, states like Florida and North Carolina exhibit more competitive support levels, with both candidates’ predicted percentages clustering around 47% to 50%.The presence of a broader range of predicted support percentages in battleground states such as Georgia and Pennsylvania reflects the volatility of voter sentiment in these regions, where Trump and Harris show closely contested support.
+The model indicates that Harris may benefit from higher support levels in traditionally Democratic states, while Trump faces a challenge in securing sufficient backing in key swing states.
+Overall, @fig-modelvisual underscore the dynamic nature of voter preferences as the election approaches, with Harris appearing to lead in overall support while Trump must contend with fluctuating voter sentiments in critical states.
+These predictions provide a view of how various factors, including time and state-specific influences, shape the electoral landscape leading up to the 2024 U.S.
+Presidential Election.
+
+## Predict Result
+```{r}
+#| echo: false
+#| eval: true
+#| label: fig-modelpctsummary
+#| fig-cap: "Summary table of average pct for each candidate by state"
+#| warning: false
+
+# Create summary table of average pct for each candidate by state
+average_pct_summary <- president_polls_cleaned_data %>%
+  group_by(state, candidate_name) %>%
+  summarise(average_pct = mean(pct, na.rm = TRUE), .groups = 'drop') %>%
+  pivot_wider(names_from = candidate_name, values_from = average_pct, 
+              names_prefix = "avg_pct_of_")
+
+# Output the table
+knitr::kable(average_pct_summary, format = "simple", col.names = c('State','PCT of Trump','PCT of Harris'))
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: fig-modelvotenum
+#| fig-cap: "Summary total votes for each candidate"
+#| warning: false
+
+# Use information from https://state.1keydata.com/state-electoral-votes.php to create dataframe
+electoral_votes <- data.frame(
+  state = c("Arizona", "California", "Connecticut", "Florida", "Georgia",
+            "Indiana", "Iowa", "Maine", "Maine CD-1", "Maine CD-2",
+            "Maine CD-3", "Maryland", "Massachusetts", "Michigan", "Minnesota", 
+            "Missouri", "Montana", "Nebraska", "Nebraska CD-1",
+            "Nebraska CD-2", "Nebraska CD-3", "Nevada", "New Hampshire", 
+            "New Mexico", "New York", "North Carolina", "Ohio", 
+            "Pennsylvania", "Rhode Island", "South Carolina", 
+            "South Dakota", "Texas", "Vermont", "Virginia", 
+            "Washington", "Wisconsin"),
+  votes = c(11, 55, 7, 29, 16, 11, 6, 4, 1, 1,
+            1, 10, 11, 15, 10, 10, 3, 5, 2, 1,
+            6, 4, 5, 29, 15, 3, 9, 4, 9, 6, 
+            13, 3, 10, 10, 8, 10)
+)
+
+# calculate total votes of each candidate
+total_votes <- average_pct_summary %>%
+  left_join(electoral_votes, by = "state") %>%
+  mutate(
+    winner = case_when(
+      average_pct_summary[2] > average_pct_summary[3] ~ "Trump",
+      average_pct_summary[2] < average_pct_summary[3] ~ "Harris",
+      TRUE ~ "Tie"  # deal with a tie
+    ),
+    winning_votes = case_when(
+      winner == "Trump" ~ votes,
+      winner == "Harris" ~ votes,
+      TRUE ~ 0
+    )
+  ) %>%
+  summarise(
+    total_trump_votes = sum(winning_votes[winner == "Trump"], na.rm = TRUE),
+    total_harris_votes = sum(winning_votes[winner == "Harris"], na.rm = TRUE)
+  )
+
+# create table of total votes
+total_votes_table <- data.frame(
+  Candidate = c("Trump", "Harris"),
+  Total_Votes = c(total_votes$total_trump_votes, total_votes$total_harris_votes)
+)
+
+knitr::kable(total_votes_table, format = "simple", col.names = c('Candidate', 'Total Votes'))
+
+```
+
+@fig-modelpctsummary produced a summary table of average support percentages for Donald Trump and Kamala Harris across various states, as well as @fig-modelvotenum predicted total vote counts based on these averages.
+@fig-modelpctsummary highlights significant differences in voter support by state, revealing regional dynamics as the election approaches.
+
+@fig-modelpctsummary indicates that Kamala Harris tends to have higher support in several key states, such as California, where she leads with an average of 59.98% compared to Donald Trump's 34.29%.
+Similarly, Maryland shows strong backing for Harris at 62.90%, while Trump receives only 32.39% of the vote.
+In contrast, Trump demonstrates stronger support in traditionally Republican-leaning states like Indiana, where he averages 57.90%, and Florida, with 51.53% support.
+The data also highlights a competitive landscape in states like Georgia and Michigan, where the candidates are closely matched; in Georgia, Harris has 47.19% compared to Trump's 48.61%, while in Michigan, Harris garners 47.84% against Trump's 46.92%.
+
+By combining the average support percentage of each state with the electoral votes in @fig-modelpctsummary, we calculated the predicted total votes of each candidate.
+Each state supports a large percentage of candidates to get the total number of votes in this state, and the total number of votes refers to @stateElectoralVotes.
+According to these calculations, @fig-modelvotenum shows that Trump got a total of 109 votes, while Harris got 222 votes.
+Thus, although both of Donald Trump and Kamala Harris is not guaranteed to win 270 votes due to lack of data in certain states, Harris has obvious advantages in the election, especially with the strong support of several key states, and predicts that she may win this election.
+
+# Discussion {#sec-discussion}
 
@@
 
-# Appendix: Idealized Methodology and Survey {#sec-Appendix2}
+# Idealized Methodology and Survey {#sec-Appendix2}
 
@@
 
-\endgroup
-
 ---

### 2024-11-04 paper/paper.qmd
update reference and discussion

@@
 ---
-title: "Forecasting the 2024 US Presidential Election"
-subtitle: "A Poll-of-Polls Approach Using Bayesian Modeling"
+title: "Predicting Electoral Outcomes: Bayesian Modeling of Voter Support Trends for Kamala Harris and Donald Trump in the 2024 Presidential Election"
+subtitle: ""
 author: 
@@
 Following the approach outlined in [@tellingstories], we aim to predict the election outcome based on this polling data.
-The analyses were conducted in R @citeR, with support from several packages.
-The `tidyverse` packages [@citetidyverse] were used in the process of data simulation, testing beforehand.
-After the original raw data was downloaded by using `tidyverse` package [@citetidyverse], data cleaning process was done by using `tidyverse` package [@citetidyverse], `lubridate` package [@citelubridate], and `arrow` package [@citearrow].
-Then, models were constructed using `tidyverse` package [@citetidyverse], `lubridate` package [@citelubridate], `rstanarm` [@citerstanarm] package, and `splines` package [@citesplines].
-The model results are then presented by `modelsummary` [@citemodelsummary] package, and graphs were made with `ggplot2` package [@citeggplot].
+The analyses were conducted in R [@citeR], utilizing several packages to streamline the process.
+The tidyverse packages [@citetidyverse] were essential for data simulation and preliminary testing.
+Initially, the raw data was downloaded using the arrow package [@citearrow], allowing for efficient handling of large datasets.
+The data cleaning process employed the dplyr [@citedplyr] and tidyr [@citetidyr] packages to reshape and organize the data effectively.
+
+Model construction involved the rstanarm [@citerstanarm] package for Bayesian regression modeling, complemented by the splines package [@citesplines] to account for non-linear relationships in the data.
+The results were summarized using the modelsummary [@citemodelsummary] package, while visualizations of the findings were created with the ggplot2 [@citeggplot] package, ensuring clear communication of the model's outputs.
 
@@
 #| fig-height: 3
-
-# Load ggplot2
-library(ggplot2)
 

### 2024-11-04 paper/paper.qmd
update title

@@
 title: "Predicting Electoral Outcomes: Bayesian Modeling of Voter Support Trends for Kamala Harris and Donald Trump in the 2024 Presidential Election"
-subtitle: ""
+subtitle: "Predictions shows higher likelyhood for Harris to be the Winner"
 author: 
@@
 ## Estimand
-
-Our primary estimand is the percentage of voter support for Donald Trump and Kamala Harris on election day.
-We estimate this support percentage both at the national level and by state, incorporating time and state-specific effects.
+Our main goal is to predict who will win the election, donald trump or Kamala Harris.
+Specifically, we estimated the voter support rate percentage of Donald Trump and Kamala Harris on election day considering sample size, state and end date, and then calculated the total number of votes obtained by Trump and Harris through the total number of votes in each state, so as to provide a reliable prediction of the election results.
 
@@
 ```
+
 @fig-modelvisual produced predicted percentages of voter support for Donald Trump and Kamala Harris over time, as shown in the graph titled "Predicted Percentage Over Time." The y-axis represents the predicted support percentage, while the x-axis indicates polling end dates.
@@
 ## Overview of the Paper
-This paper presents a comprehensive analysis of polling data to forecast support for candidates Kamala Harris and Donald Trump in the upcoming U.S.
-presidential election.
-By employing a Bayesian linear regression model, the study investigates how various factors such as polling date, candidate identity, sample size, and geographic location influence voter support.
-The findings contribute to understanding the dynamics of electoral support and the effectiveness of polling methodologies in predicting election outcomes.
-
-## Insights About the World
-One significant insight derived from this analysis is the importance of temporal dynamics in voter support.
+This study employs a Bayesian modeling approach to forecast the 2024 U.S.
+presidential election, focusing on the candidates Kamala Harris and Donald Trump.
+By analyzing a comprehensive dataset of high-quality polls, the paper identifies the dynamics of voter support and how various factors—such as polling methodology, sample size, and geographic location—influence electoral outcomes.
+The findings indicate a greater likelihood of victory for Harris, projecting her with 222 electoral votes compared to Trump’s 109.
+
+## Findings About the World
+One finding from this analysis is the importance of temporal dynamics in voter support.
 The model highlights that the timing of polling can substantially impact the reported support for candidates.
 This finding suggests that voters’ preferences are not static; rather, they fluctuate based on current events, campaign strategies, and media coverage.
-Such insights underscore the need for political strategists and candidates to consider timing when conducting polls and planning campaign efforts.
-
-Another critical takeaway is the varying levels of support for candidates across different states.
-The analysis reveals regional disparities in voter sentiment, indicating that geographic factors significantly influence political preferences.
-This highlights the importance of localized campaign strategies and targeted outreach, as what resonates in one state may not hold true in another.
-Understanding these regional differences can enhance candidates' ability to connect with voters and tailor their messaging effectively.
+This underscore the need for political strategists and candidates to consider timing when conducting polls and planning campaign efforts.
+
+Another finding is the diverse levels of candidate support across states.
+The analysis shows that voter sentiment differs by region, suggesting that geographic factors shape political preferences.
+This underscores the value of tailoring campaign efforts to specific areas, as messages that appeal to one state may not be as effective in another.
+Recognizing these regional differences allows candidates to better engage with voters and adapt their messaging to local priorities
 
 ## Limitations of the Study
-Despite its contributions, the study is not without weaknesses.
-One notable limitation is the reliance on existing polling data, which may introduce biases if the data collection methods are not standardized across pollsters.
-Variations in methodology, sample demographics, and question phrasing can lead to discrepancies in reported support levels.
-Additionally, the model assumes a linear relationship between predictors and outcomes, which may oversimplify the complexities of voter behavior.
-A more nuanced approach that incorporates non-linear effects or interactions between variables could provide deeper insights into voter dynamics.
+Despite its contributions, this study has limitations.
+The reliance on existing polling data introduces potential biases, as varying methodologies among pollsters can lead to discrepancies in reported support levels.
+Additionally, the model's assumption of a linear relationship between predictors and outcomes may oversimplify the complexities of voter behavior.
+
+Another limitation is the lack of a time series analysis.
+While the study captures snapshots of voter sentiment at specific moments, it does not account for how trends develop over time.
+This oversight may obscure patterns of voter behavior that emerge as the election date approaches.
+Future research should incorporate time series methodologies to better understand how public opinion evolves and to identify trends that could inform campaign strategies.
+
+Moreover, the exclusion of demographic factors such as age, income, and education could further explain variations in voter support.
+Incorporating these elements into future models may improve the robustness of electoral predictions.
 
 ## Future Directions
-Looking ahead, several avenues for further research emerge from this study.
-First, it would be valuable to explore the impact of specific events, such as debates or major news stories, on voter sentiment.
-Incorporating real-time data and sentiment analysis from social media could enrich the understanding of how public opinion shifts in response to external influences.
-Furthermore, expanding the model to include demographic factors—such as age, income, and education—could yield a more comprehensive picture of voter support and the diverse motivations behind electoral choices.
-
-In conclusion, while this paper offers valuable insights into electoral dynamics, it also highlights the complexities of voter behavior and the need for continued exploration in this field.
-Future research should strive to incorporate a broader range of variables and methodologies to enhance the predictive accuracy of electoral forecasts and better inform political strategy.
+Future research could investigate the effects of significant events, such as presidential debates or major political announcements, on voter sentiment over time.
+Incorporating time series analysis would allow for examination of how public opinion shifts in response to these events and help identify patterns that develop as the election date approaches.
+
+Additionally, integrating real-time social media analysis and sentiment tracking could provide a clearer view of how public opinion changes in response to external factors.
+Expanding the model to include demographic variables, such as age, income, and education, would enhance understanding of voter behavior and the reasons behind electoral choices.
+
+Overall, these approaches would strengthen the analysis and assist political strategists in adapting to changes in voter sentiment more effectively.
 

### 2024-11-04 paper/paper.qmd
add comment in script and more graphs in data section

@@
 library(arrow)
+library(janitor)
+library(lubridate)
+library(broom)
+library(modelsummary)
+library(splines)
+library(caret)
 ```
@@
 The tidyverse packages [@citetidyverse] were essential for data simulation and preliminary testing.
-Initially, the raw data was downloaded using the arrow package [@citearrow], allowing for efficient handling of large datasets.
-The data cleaning process employed the dplyr [@citedplyr] and tidyr [@citetidyr] packages to reshape and organize the data effectively.
-
-Model construction involved the rstanarm [@citerstanarm] package for Bayesian regression modeling, complemented by the splines package [@citesplines] to account for non-linear relationships in the data.
-The results were summarized using the modelsummary [@citemodelsummary] package, while visualizations of the findings were created with the ggplot2 [@citeggplot] package, ensuring clear communication of the model's outputs.
+Initially, the raw data was downloaded using the arrow package [@citearrow], which facilitated efficient handling of large datasets.
+
+Data cleaning employed dplyr [@citedplyr], tidyr [@citetidyr], and janitor [@citejanitor] to ensure consistent data structure, particularly for renaming columns and removing inconsistencies.
+Date variables were managed with the lubridate package [@citelubridate], making it easier to handle time-based data accurately.
+For modeling, rstanarm [@citerstanarm] was used for Bayesian regression modeling, while splines [@citesplines] handled non-linear relationships, and caret [@citecaret] supported model training and validation.
+The modelsummary [@citemodelsummary] package was used to summarize results, and broom [@citebroom] helped tidy up model outputs.
+Lastly, ggplot2 [@citeggplot] generated clear visualizations, ensuring effective communication of the findings.
 
@@
 ## Predictors Explanation
-- **state**: The U.S. state where the poll was conducted, which allows for state-by-state analysis and comparison of support levels.
-
-- **end date**: The date the poll concluded, marking the end of data collection for that specific poll.
+- **end date**: The date the poll concluded, marking the end of data collection for that specific poll.In the context of our analysis, we have set a criterion whereby the end dates must be greater than July 21, 2024.
+This threshold ensures that we are only considering the most recent and relevant polling data as we approach the 2024 election cycle.
+
+- **candidate_name**: The name of the candidate being polled, which in this data set focuses on Donald Trump and Kamala Harris.
+
+- **state**: The U.S.
+state where the poll was conducted, which allows for state-by-state analysis and comparison of support levels.
+@fig-state indicates the distribution of states.The histogram shows the distribution of polling data across different states.
+States like California and Georgia have high counts, indicating overrepresentation, while states such as Wyoming and South Dakota are underrepresented.
+
+```{r}
+#| label: fig-state
+#| fig-cap: Distribution of State
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 10
+#| fig-height: 6
+
+ggplot(president_polls_cleaned_data, aes(x = state)) +
+  geom_bar(fill = "pink") +
+  labs(x = "State",
+       y = "Count") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Adjust text angle for better readability
+```
 
 - **sample size**: The number of respondents in the poll, indicating the scope and potential statistical reliability of the results.
-
-- **candidate_name**: The name of the candidate being polled, which in this data set focuses on Donald Trump and Kamala Harris.
+@fig-samplesize shows that smaller sample sizes (0 to 500) are significantly more common, indicating a high concentration of data points in this range and these specific sizes are frequently represented in the polling data, while larger sample sizes are relatively scarce.
+```{r}
+#| label: fig-samplesize
+#| fig-cap: Distribution of Sample Size
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 6
+#| fig-height: 3
+
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+
+# Create a summary of counts for each sample_size
+sample_size_summary <- president_polls_cleaned_data %>%
+  group_by(sample_size) %>%
+  summarise(count = n())
+
+# Create a line plot of sample_size
+ggplot(sample_size_summary, aes(x = sample_size, y = count)) +
+  geom_line(color = "pink") +
+  geom_point(color = "lightblue") +  # Optional: add points to highlight each count
+  theme_minimal() +
+  labs(#title = "Line Plot of Sample Size Counts",
+       x = "Sample Size",
+       y = "Count") 
+#+ theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Adjust text angle for better readability
+
+```
 
@@
 - **numeric grade**: A quality score assigned to the pollster, with higher values indicating greater reliability. Only pollsters with a score above 2.5 are included to enhance accuracy.
-
-- **pollscore**: A specific rating of the individual poll, reflecting additional factors that impact the poll's quality and reliability.
-
-- **methodology**: The method used by the pollster to conduct the poll, which may affect the reliability and interpretation of the results.
-
-- **transparency score**: A measure of how openly the pollster reports their methodology and results. Higher scores suggest greater transparency and reliability.
 
@@
     y = "Percentage",
-    title = "Predicted Percentage Over Time",
+    #title = "Predicted Percentage Over Time",
     color = "Candidate",
@@
 This study employs a Bayesian modeling approach to forecast the 2024 U.S.
-presidential election, focusing on the candidates Kamala Harris and Donald Trump.
-By analyzing a comprehensive dataset of high-quality polls, the paper identifies the dynamics of voter support and how various factors—such as polling methodology, sample size, and geographic location—influence electoral outcomes.
-The findings indicate a greater likelihood of victory for Harris, projecting her with 222 electoral votes compared to Trump’s 109.
+presidential election, focusing on candidates Kamala Harris and Donald Trump.
+By analyzing a robust dataset of high-quality polls, the research investigates how factors such as polling methodology, sample size, and geographic location influence voter support.
+The findings indicate that Harris is projected to secure 222 electoral votes, while Trump is expected to receive 109.
+
+These results reflect broader social dynamics that shape electoral behavior.
+Variations in support across states suggest that regional identities and socio-political contexts significantly influence public opinion.
+Research indicates that diverse populations often favor candidates advocating for progressive policies, which align with issues such as racial equity, healthcare access, and economic opportunity (@pew2020).
+Conversely, more conservative regions tend to support traditional Republican platforms, reflecting local values and priorities (@brookings2020).
 
@@
 By applying probability sampling, each individual has a known chance of selection, allowing the results to be statistically valid and generalizable.
-This design accounts for demographic, geographic, and political influences, enhancing prediction reliability [@fivethirty; @pewresearch].
+This design accounts for demographic, geographic, and political influences, enhancing prediction reliability [@fivethirtyeight; @pewresearch].
 
@@
 \newpage
-
-# Additional data details
-
 # Model details {#sec-model-details}
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheck
+#| fig-width: 6
+#| fig-height: 4
+#| fig-cap: "Posterior Predictive Check of Bayesian Models"
+
+# Load the model using the here function to specify the path
+model_bayes <- readRDS("../models/election_glm_model.rds")
+# Perform posterior predictive check
+pp_check(model_bayes)
+```
+
+@fig-ppcheck presents a posterior predictive check (PPC) for Bayesian model, illustrating the relationship between the observed data and the data replicated by the model.
+On the x-axis, the values of the response variable are depicted, while the y-axis indicates the density or probability of those values.
+The dark blue curve represents the observed data, denoted as $y$, and is contrasted with multiple light blue curves that signify the model's replicated data, referred to as $y_rep$.
+The close overlap between the dark blue curve and the cluster of light blue curves suggests that the model fits the observed data well, indicating its ability to replicate the distribution of the data accurately.
+Additionally, the variability among the light blue curves highlights the uncertainty in the model's predictions; if these curves were excessively dispersed or showed minimal overlap with the observed data, it would signal potential issues with the model's fit.
 
 ## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+### R-hat Plots
+
+$\hat{R}$ is a diagnostic measure that compares the variance within each chain to the variance between chains.
+@fig-rhat presents the R-hat values for Bayesian model, which serves as a diagnostic indicator for evaluating the convergence of Markov Chain Monte Carlo (MCMC) chains.
+The x-axis indicates the R-hat statistic, reflecting the convergence status of each parameter in the model, while the y-axis lacks a specific scale and displays various R-hat values along a vertical line.
+Each point represents the R-hat value for a different parameter, and their clustering around 1.00 suggests effective convergence.
+Additionally, @fig-rhat includes interpretation thresholds for R-hat values: values at or below 1.05 signify satisfactory convergence, while values up to 1.1 may indicate some potential convergence issues but are generally considered acceptable.
+In contrast, values exceeding 1.1 suggest poor convergence, indicating that further iterations may be necessary to obtain stable estimates.
+Since most of the R-hat values in @fig-rhat are well below 1.05, we can infer that the Bayesian model that we construnct is likely well-fitted and does not raise significant concerns regarding the convergence of the MCMC process.
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-rhat
+#| fig-cap: "R-hat Plots of Bayesian Model"
+#| fig-width: 6
+#| fig-height: 4
+
+plot(model_bayes, "rhat")
+
+```
+
+### Trace Plots
+
+Trace plot of  Bayesian model illustrates the sampled values of various parameters across multiple iterations of the Markov Chain Monte Carlo (MCMC) process, and discusses the convergence of the MCMC chains.
+Organized in a grid format, each row represents a different parameter, while each column corresponds to a specific MCMC chain.
+The x-axis indicates the iteration number of the MCMC sampling, and the y-axis shows the values of the parameters being sampled, with different colors or line styles potentially representing various MCMC chains.
+Ideally, the sampled values should fluctuate around a stable mean, indicating effective convergence.
+Conversely, if any parameter shows a lack of mixing or clear trends, such as drifting over time, it may indicate convergence issues, necessitating additional iterations or adjustments to improve the model.
+
+@fig-trace presents a trace plot for the Bayesian model which consider different states, variable end date, variable sample size and variable candidate name.
+We can see that there is no clear separation between the chains and sampled values fluctuate around the stable mean, suggesting the MCMC sampling has successfully converged for most parameters.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: fig-trace
+#| fig-cap: "Trace Plot of Bayesian Model"
+#| warning: false
+#| fig-width: 12
+#| fig-height: 12
+
+plot(model_bayes, "trace")
+```
 

### 2024-11-04 scripts/00-simulate_data.R

@@ -17,23 +17,6 @@ set.seed(666)
 num_rows <- 100  # Number of simulated rows
 
 simulated_president_polls <- data.frame(
-  # pollster = sample(c("Emerson", "YouGov", "Beacon/Shaw", "Quinnipiac", "SurveyUSA", "East Carolina University", "Fairleigh Dickinson", "Ipsos", "Marist", "Siena/NYT", "University of Massachusetts Lowell/YouGov", "Marquette Law School", "Hart/POS", "The Washington Post", "Pew", "Suffolk", "Mason-Dixon",
-                      #"Christopher Newport U.", "Data for Progress", "YouGov/Center for Working Class Politics", "UC Berkeley", "Winthrop U.", "High Point University", "McCourtney Institute/YouGov", "Echelon Insights", "CNN/SSRS", "AtlasIntel", "University of Maryland/Washington Post", "Remington", "Muhlenberg", 
-                      #"MassINC Polling Group", "U. New Hampshire",  "Siena", "Elon U.", "Selzer", "Data Orbital", "PPIC", "Washington Post/George Mason University", "Kaiser Family Foundation", "SurveyUSA/High Point University", "Roanoke College", "YouGov Blue", "U. North Florida"), num_rows, replace = TRUE),
-  # numeric_grade = sample(2:3, num_rows, replace = TRUE),  # Numeric grades between 1 and 5
-  # pollscore = rnorm(num_rows, mean = -1, sd = 0.5),  # Normally distributed poll scores
-  # methodology = sample(c("IVR/Online Panel/Text-to-Web", "Online Panel", "IVR/Online Panel", "Live Phone/Text-to-Web",
-                         #"Live Phone", "IVR/Text-to-Web", "Probability Panel", "Online Panel/Text-to-Web", 
-                         #"Live Phone/Online Panel/Text-to-Web", "Email", "Live Phone/Online Panel",
-                         #"Live Phone/Text-to-Web/Email/Mail-to-Web/Mail-to-Phone", "Online Ad"
-                         #,"Live Phone/Online Panel/Text", "Live Phone/Email", "Live Phone/Probability Panel", "IVR")
-                       #, num_rows, replace = TRUE),  # Poll methodologies
-  # transparency_score = runif(num_rows, min = 1, max = 10),  # Uniform transparency scores between 1 and 10
-  # population = sample(c("lv", "rv"), num_rows, replace = TRUE),  # Random population groups
[…]

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -12,6 +12,7 @@
 library(tidyverse)
 library(arrow)
 
+#import simulated data
 analysis_data <- read_parquet("data/00-simulated_data/simulated_president_polls.parquet")
 
 # Test if the data was successfully loaded
@@ -23,7 +24,6 @@ if (exists("analysis_data")) {
 
 
 #### Test data ####
-
 # Check if the dataset has 100 rows
 if (nrow(analysis_data) == 100) {
   message("Test Passed: The dataset has 100 rows.")

### 2024-11-04 scripts/02-download_data.R

@@ -9,8 +9,8 @@
 
 #### Workspace setup ####
 library(tidyverse)
-
+#### Download Data ####
 president_polls_raw_data <- read_csv("https://projects.fivethirtyeight.com/polls/data/president_polls.csv")
+
 #### Save data ####
-# change the_raw_data to whatever name you assigned when you downloaded it.
 write_parquet(president_polls_raw_data, "data/01-raw_data/president_polls.parquet")

### 2024-11-04 scripts/03-clean_data.R

@@ -14,33 +14,30 @@ library(tidyr)
 library(arrow)
 
 #### Clean data ####
-president_polls_raw_data <- read_parquet('data/01-raw_data/president_polls.parquet')
+president_polls_raw_data <- read_parquet('data/01-raw_data/president_polls.parquet') # import raw data
 
-# filter out high quality polls（numeric_grade >= 2.5)
 president_polls_filtered <- president_polls_raw_data %>% 
-  janitor::clean_names() %>%
-  select(# pollscore, methodology, transparency_score, start_date, population, population_full, hypothetical, answer, pollster,
+  janitor::clean_names() %>% # correct name to standard form
+  select( # only keep needed columns
     numeric_grade,
     state, 
     end_date, 
     sample_size,
     candidate_name, 
     pct) %>%
-  tidyr::drop_na()
+  tidyr::drop_na() # eliminate date that is null
 
 president_polls_cleaned_data <- president_polls_filtered %>%
   mutate(
-    # hypothetical = ifelse(hypothetical == 'true', 1, 0),start_date = mdy(start_date),
     state = if_else(is.na(state) | state == "", "National", state), 
     end_date = mdy(end_date),
-    # num_candidates = round((pct / 100) * sample_size, 0)
 ) %>%
-  filter(numeric_grade >= 2.5
-         , candidate_name %in% c("Kamala Harris", "Donald Trump")
-         , end_date >= as.Date("2024-07-21")
+  filter(numeric_grade >= 2.5 # filter out high quality polls（numeric_grade >= 2.5)
+         , candidate_name %in% c("Kamala Harris", "Donald Trump") # filter out data of Kamala Harris and Donald Trump
+         , end_date >= as.Date("2024-07-21") # filter out data after byden was out
          , !is.na(end_date)  # eliminate date that is null
 ) %>%
-  select(# pollscore, methodology, transparency_score, start_date, population, population_full, hypothetical, answer, pollster,
+  select( # only keep needed columns
     state, 
     end_date, 
     sample_size,

### 2024-11-04 scripts/04-test_analysis_data.R

@@ -12,18 +12,17 @@ library(tidyverse)
 library(testthat)
 library(arrow)
 
+#import analysis data
 analysis_data <- read_parquet("data/02-analysis_data/president_polls_cleaned_data.parquet")
 
 
 #### Test data ####
-
 # Check if the dataset has 5 columns
 if (ncol(analysis_data) == 5) {
   message("Test Passed: The dataset has 5 columns.")
 } else {
   stop("Test Failed: The dataset does not have 5 columns.")
 }
-
 
 # Check if the 'state' column contains only valid Australian state names
 valid_states <- c("National", "Arizona", "California", "Georgia", "North Carolina", 

### 2024-11-04 paper/paper.qmd
delete some words for prose

@@
 date-format: long
-abstract: "This paper builds a predictive Bayesian model to forecast the 2024 US presidential election using a “poll-of-polls” approach, analyzing high-quality polls for Kamala Harris and Donald Trump.
+abstract: "This paper builds a predictive Bayesian model to forecast the 2024 US presidential election using a poll-of-polls approach, analyzing high-quality polls for Kamala Harris and Donald Trump.
 The model incorporates data on polling methodology, state trends, and candidate support.
@@
 presidential election is generating significant public interest, with recent polling reflecting shifts in candidate support across various demographic and regional groups.
-Polling data, while insightful, presents challenges due to inherent biases, variability in polling methodology, and regional influences on voter behavior.
-This study aims to address these challenges using a "poll-of-polls" approach, aggregating high-quality national and state polls to forecast voter support for Kamala Harris and Donald Trump.
+Polling data presents challenges due to inherent biases, variability in polling methodology, and regional influences on voter behavior.
+This study aims to address these challenges using a poll-of-polls approach, aggregating high-quality national and state polls to forecast voter support for Kamala Harris and Donald Trump.
 By applying Bayesian modeling, this analysis incorporates both the temporal dynamics of candidate support and state-specific trends.
@@
 The results, visualized in @fig-modelvisual, indicate stable support for Harris at an estimated 52% nationally, with a confidence interval of approximately 49% to 55%.
-Trump’s predicted support level centers around 46%, with a range of about 43% to 49%, showing a slight downward trend as the election date nears.
+Trump’s predicted support level centers around 46%, with a range of about 43% to 49%, showing a decreasing trend as the election date nears.
 State-specific polling results highlight variances, with Harris showing stronger support in traditionally Democratic areas like Maine CD-1, where predicted support reaches around 62%.
@@
 @sec-result presents our main results, including both the model's outputs and the predictions of voter support for the key candidates.
-In @sec-discussion, we discuss the findings, offer insights into the broader implications, and highlight the limitations and potential directions for future research.
-Finally, the appendices provide additional methodological analysis, an idealized survey methodology, and supporting details for the data and model diagnostics.
+In @sec-discussion, we discuss the findings, give broader implications, and highlight the limitations and potential directions for future research.
+Finally, the appendices provide additional methodological analysis, an idealized survey methodology, and model diagnostics.
 
 ## Estimand
-Our main goal is to predict who will win the election, donald trump or Kamala Harris.
+Our main goal is to predict who will win the election, Donald trump or Kamala Harris.
 Specifically, we estimated the voter support rate percentage of Donald Trump and Kamala Harris on election day considering sample size, state and end date, and then calculated the total number of votes obtained by Trump and Harris through the total number of votes in each state, so as to provide a reliable prediction of the election results.
@@
 The data cleaning process standardizes column names, retains relevant fields, and addresses missing values to ensure high-quality data for analysis.
-The section includes a table presenting the first six entries of the cleaned analysis dataset, alongside multiple graphs: a bar graph comparing candidate support percentages by state, scatter plots illustrating trends in candidate support over time, and visualizations examining the relationship between sample size and support percentages.
-
-The analysis utilizes FiveThirtyEight's dataset of national presidential general election polls [@fivethirtyeight].
+The section includes a table presenting the first six entries of the cleaned analysis data set, alongside multiple graphs: a bar graph comparing candidate support percentages by state, scatter plots illustrating trends in candidate support over time, and visualizations examining the relationship between sample size and support percentages.
+
+The analysis utilizes FiveThirtyEight's data set of national presidential general election polls [@fivethirtyeight].
 Following the approach outlined in [@tellingstories], we aim to predict the election outcome based on this polling data.
@@
 @fig-state indicates the distribution of states.The histogram shows the distribution of polling data across different states.
-States like California and Georgia have high counts, indicating overrepresentation, while states such as Wyoming and South Dakota are underrepresented.
+States like California and Georgia have high counts, indicating over representation, while states such as Wyoming and South Dakota are underrepresented.
 
@@
 The mathematical formulation allows for the representation of the intercept, which denotes the baseline support level, alongside coefficients that quantify the influence of each predictor.
-The priors assigned to the model parameters are carefully chosen to reflect reasonable expectations based on historical voting patterns, thus enhancing the model's interpretability and effectiveness.
+The priors assigned to the model parameters are carefully chosen to reflect reasonable expectations based on historical voting patterns, thus enhancing the model's interpret ability and effectiveness.
 Moreover, the Bayesian framework enables the modeling of potential interactions between state-specific effects and candidate support, allowing us to capture the regional variations that are often observed in electoral outcomes.
 By incorporating individual pollster effects as fixed coefficients, we can account for the inherent biases associated with different polling organizations, ensuring that our model provides a nuanced view of candidate support.
-This model's formulation strikes a balance between complexity and interpretability, allowing for a comprehensive analysis of the factors influencing voter sentiment while maintaining computational efficiency.
+This model's formulation strikes a balance between complexity and interpret ability, allowing for a comprehensive analysis of the factors influencing voter sentiment while maintaining computational efficiency.
 The Bayesian approach not only enhances our understanding of electoral dynamics but also provides a statistically sound basis for forecasting potential election outcomes.

### 2024-11-04 paper/paper.qmd
replace word and correct typo

@@
 - **state**: The U.S.
-state where the poll was conducted, which allows for state-by-state analysis and comparison of support levels.
+state where the poll was conducted, which allows for state by state analysis and comparison of support levels.
 @fig-state indicates the distribution of states.The histogram shows the distribution of polling data across different states.
@@
 pct is the support percentage each candidate received in the poll, which serves as the outcome variable for analysis.
-This variable is crucial for understanding the electoral dynamics, as it quantifies the level of public backing for each candidate at a given time and place.
+This variable is important for understanding the electoral dynamics, as it quantifies the level of public backing for each candidate at a given time and place.
 By analyzing the pct variable, researchers can assess trends in voter sentiment, compare the effectiveness of campaign strategies, and identify which demographic groups are more inclined to support one candidate over the other.
 Additionally, fluctuations in the pct can signal shifts in public opinion that may correlate with significant political events, media coverage, or changes in candidates' messaging.
-This outcome variable allows for a comprehensive analysis of the electoral landscape, providing insights into how various factors influence voter behavior and preferences throughout the campaign.
+This outcome variable allows for a comprehensive analysis of the electoral landscape, providing understandings into how various factors influence voter behavior and preferences throughout the campaign.
 
@@
 It provides snapshots of voter sentiment at specific times rather than ongoing updates, potentially missing rapid shifts in public opinion, especially near Election Day.
-Adjustments are made for recency, but participation and response biases—like self-selection and social desirability bias—can still impact accuracy by creating gaps between expressed opinions and actual voting behavior.
-Additionally, regional polling disparities, with battleground states polled more frequently than “safe” states, can lead to imbalances in representation, highlighting the challenge of achieving uniformly accurate forecasts across the nation.
+Adjustments are made for recenct situations, but participation and response biases—like self-selection and social desirability bias—can still impact accuracy by creating gaps between expressed opinions and actual voting behavior.
+Additionally, regional polling disparities, with battleground states polled more frequently than "safe" states, can lead to imbalances in representation, highlighting the challenge of achieving uniformly accurate forecasts across the nation.
 
@@
 The y-axis shows support percentages up to around 70%, while the x-axis lists states, each with two bars per candidate.
-@fig-pct-state reveals regional popularity variations.
+@fig-pct-state indicates regional popularity variations.
 In some states, bars for both candidates are nearly equal in height, indicating competitive support.
@@
 The visualization shows fluctuating support levels for both candidates, with Harris generally receiving higher support in states like California and New York, whereas states like Florida and Indiana display a more competitive landscape.
-The national plot reveals trends in support, reflecting periods of gain or loss for both candidates, suggesting that voter sentiment is dynamic and influenced by external factors during the campaign.
+The national plot shows trends in support, reflecting periods of gain or loss for both candidates, suggesting that voter sentiment is dynamic and influenced by external factors during the campaign.
 Overall, the figure highlights the changing electoral support for Trump and Harris across states and time.
@@
 **Normality of Errors**: It is assumed that the residuals (the differences between observed and predicted values) follow a normal distribution.
-This assumption is crucial for making valid inferences; violations can lead to incorrect conclusions and unreliable credible intervals.
+This assumption is important for making valid inferences; violations can lead to incorrect conclusions and unreliable credible intervals.
 Diagnostic checks and posterior predictive checks are used to assess model fit and adherence to assumptions.
@@
 This choice of modeling framework is particularly suitable for our objectives, as it allows for the incorporation of prior knowledge regarding electoral dynamics while updating predictions based on newly observed data.
-The Bayesian approach provides a robust mechanism for estimating uncertainty in our predictions, which is crucial in the context of political polling where public sentiment can fluctuate significantly.
+The Bayesian approach provides a robust mechanism for estimating uncertainty in our predictions, which is important in the context of political polling where public sentiment can fluctuate significantly.
 The model structure includes key predictors: the polling end date, candidate name, sample size, and state.
@@
 The Bayesian approach not only enhances our understanding of electoral dynamics but also provides a statistically sound basis for forecasting potential election outcomes.
-Overall, the chosen model is well-aligned with the objectives of this study, facilitating a robust analysis of polling data to derive meaningful insights into the upcoming election.
+Overall, the chosen model is well-aligned with the objectives of this study, facilitating a robust analysis of polling data to derive meaningful understandings into the upcoming election.
 
@@
 
-@tbl-modelresults provide insights into the factors influencing voter support for Donald Trump and Kamala Harris, based on a total of 846 observations.
+@tbl-modelresults provide understandings into the factors influencing voter support for Donald Trump and Kamala Harris, based on a total of 846 observations.
 The model intercept is estimated at -397.72, serving as a baseline from which other coefficients are interpreted.
@@
 Additionally, the root mean square error (RMSE) of 4.18 suggests that the predicted percentages deviate from actual support levels by approximately 4.18 percentage points on average.
-Overall, these results underscore the importance of both temporal dynamics and regional differences in predicting voter support, while also indicating a need for further exploration of additional variables that may more effectively account for observed voter preferences.
+Overall, these results underscore the importance of both temporal dynamics and regional differences in predicting voter support, while also indicating a need for further study of additional variables that may more effectively account for observed voter preferences.
 
@@
 @fig-modelvisual produced predicted percentages of voter support for Donald Trump and Kamala Harris over time, as shown in the graph titled "Predicted Percentage Over Time." The y-axis represents the predicted support percentage, while the x-axis indicates polling end dates.
-@fig-modelvisual reveals distinct trends in voter support for both candidates.
+@fig-modelvisual indicates distinct trends in voter support for both candidates.
 The predictions for Kamala Harris (shown in teal) suggest a mean support level consistently around 52% during this period, with the confidence interval shaded in gray indicating a range from approximately 49% to 55%.
@@
 The model indicates that Harris may benefit from higher support levels in traditionally Democratic states, while Trump faces a challenge in securing sufficient backing in key swing states.
-Overall, @fig-modelvisual underscore the dynamic nature of voter preferences as the election approaches, with Harris appearing to lead in overall support while Trump must contend with fluctuating voter sentiments in critical states.
+Overall, @fig-modelvisual underscore the dynamic nature of voter preferences as the election approaches, with Harris appearing to lead in overall support while Trump must contend with fluctuating voter sentiments in swing states.
 These predictions provide a view of how various factors, including time and state-specific influences, shape the electoral landscape leading up to the 2024 U.S.
@@
 @fig-modelpctsummary produced a summary table of average support percentages for Donald Trump and Kamala Harris across various states, as well as @fig-modelvotenum predicted total vote counts based on these averages.
-@fig-modelpctsummary highlights significant differences in voter support by state, revealing regional dynamics as the election approaches.
+@fig-modelpctsummary highlights significant differences in voter support by state, indicateing regional dynamics as the election approaches.
 
@@
 presidential election, focusing on candidates Kamala Harris and Donald Trump.
-By analyzing a robust dataset of high-quality polls, the research investigates how factors such as polling methodology, sample size, and geographic location influence voter support.
+By analyzing the dataset of high-quality polls, the research investigates how factors such as polling methodology, sample size, and geographic location influence voter support.
 The findings indicate that Harris is projected to secure 222 electoral votes, while Trump is expected to receive 109.
@@
   - **Public voter registration records**: These ensure that the survey captures a valid sample of registered voters, allowing for accurate political representation.
-  - **2020 Current Population Survey (CPS)** and **National Election Pool (NEP) exit polls**: These sources offer insights into voting behaviors and preferences, enriching the sampling frame with relevant context and historical data.
+  - **2020 Current Population Survey (CPS)** and **National Election Pool (NEP) exit polls**: These sources offer understandings into voting behaviors and preferences, enriching the sampling frame with relevant context and historical data.
 
@@
   - **Clarity and Relevance**: Questions were designed to be straightforward, addressing current political concerns likely to engage respondents effectively.
-  - **Comprehensive Coverage**: The questionnaire covered a wide array of topics pertinent to the election, providing rich data for analysis and ensuring relevant insights into voter sentiment.
+  - **Wide Coverage**: The questionnaire covered a wide array of topics pertinent to the election, providing rich data for analysis and ensuring relevant understandings into voter sentiment.
 
@@
 
-2. **Improved Matching Techniques**: Exploring advanced statistical techniques or machine learning approaches for matching respondents could enhance the accuracy of the matched sample.
+2. **Improved Matching Techniques**: Exploring statistical techniques or machine learning approaches for matching respondents could enhance the accuracy of the matched sample.
 
@@
 However, inherent challenges associated with opt-in panels, matching techniques, and questionnaire design warrant careful consideration.
-By addressing these weaknesses and implementing the suggested improvements, the reliability and validity of future surveys can be enhanced, ultimately providing richer insights into voter behavior and preferences.
+By addressing these weaknesses and implementing the suggested improvements, the reliability and validity of future surveys can be enhanced, ultimately providing richer understandings into voter behavior and preferences.
 
@@
 ### Core Objectives
-- **Representative Sampling**: Achieve a sample reflecting U.S. voting demographics, ensuring insights are applicable to the entire electorate.
+- **Representative Sampling**: Achieve a sample reflecting U.S. voting demographics, ensuring understandings are applicable to the entire electorate.
 - **Data Quality**: Implement validation processes, including cross-verification, to ensure accuracy.
@@
 ## Sampling Strategy
-The sampling strategy combines **stratified random sampling** and **quota sampling** for comprehensive representation across key demographics.
+The sampling strategy combines **stratified random sampling** and **quota sampling** for representation across key demographics.
 Stratified random sampling ensures each subgroup within the population is represented by dividing the population into strata (e.g., age, gender, race) and sampling randomly within each stratum.
@@
 
-**Section 5: Additional Insights**
+**Section 5: Additional understandings**
 
@@
 
-Do you have any further comments or insights about the factors that might affect the 2024 U.S. Presidential Election? (optional)
+Do you have any further comments about the factors that might affect the 2024 U.S. Presidential Election? (optional)
 
@@
 We appreciate your time and thoughtful responses.
-Your participation is invaluable in helping us gather insights for our research on the 2024 U.S.
+Your participation is invaluable in helping us gather understandings for our research on the 2024 U.S.
 Presidential Election forecast.

### 2024-11-04 scripts/02-download_data.R
change raw data to csv

@@ -13,4 +13,4 @@ library(tidyverse)
 president_polls_raw_data <- read_csv("https://projects.fivethirtyeight.com/polls/data/president_polls.csv")
 
 #### Save data ####
-write_parquet(president_polls_raw_data, "data/01-raw_data/president_polls.parquet")
+write_csv(president_polls_raw_data, "data/01-raw_data/president_polls.csv")

### 2024-11-04 scripts/03-clean_data.R

@@ -14,7 +14,7 @@ library(tidyr)
 library(arrow)
 
 #### Clean data ####
-president_polls_raw_data <- read_parquet('data/01-raw_data/president_polls.parquet') # import raw data
+president_polls_raw_data <- read_csv('data/01-raw_data/president_polls.csv') # import raw data
 
 president_polls_filtered <- president_polls_raw_data %>% 
   janitor::clean_names() %>% # correct name to standard form
